---
title: "Data Exploration exp-01 pilot-01"
format:
  html:
    code-fold: true

---

This is an exploratory analysis pipeline, using data collected from Prolific on (N=10).
```{r}
#| echo: true
#| warning: false


# load packages
library(pacman)
p_load(tidyverse, ggbeeswarm, brms, tidyboot, tidyjson, tidybayes, patchwork, GGally, cowplot, BayesFactor, aida, faintr, cspplot, knitr, patchwork, here)

##################################################

# these options help Stan run faster
options(mc.cores = parallel::detectCores(),
        brms.backend = "cmdstanr")

# use the CSP-theme for plotting
theme_set(theme_csp())

# global color scheme from CSP
project_colors = cspplot::list_colors() |> pull(hex)

# setting theme colors globally
scale_colour_discrete <- function(...) {
  scale_colour_manual(..., values = project_colors)
}

scale_fill_discrete <- function(...) {
  scale_fill_manual(..., values = project_colors)
}

##################################################
```
## Preprocessing
First, we clean up the data by renaming columns and removing empty rows. We start preparing for data exclusion by
logging correctness of all comprehension responses.
```{r}
raw <- as_tibble(read.csv(here("01-experiments","03-phase-speaker-and-listener-oriented","01-exp-prescrNorm-speakerListener","01 data","results_pilot-01.csv")))

full <- raw %>%
  rename(trial_type = trialType) %>%
  rename(trial_nr = trialNr) %>%
  select(where(~!all(is.na(.)))) %>%
  mutate(correct = ifelse(is.na(correct_response), TRUE, correct_response == response))
```

## Exclusion
We exclude from further analysis participants who didn't pass the first set of comprehension questions even on their
second attempt or failed more than one question from the second set of comprehension questions.
```{r}
getComprehensionPass <- function(id) {
  participant <- full %>% filter(prolific_pid == id)
  comp1 <- participant %>%
    filter(trial_type %in% c("comprehension-1-1", "comprehension-1-2")) %>%
    group_by(trial_type) %>%
    summarise(all_correct = all(correct), .groups = "drop") %>%
    arrange(trial_type) %>%
    pull(all_correct)

  comp2 <- participant %>%
    filter(trial_type == 'comprehension-2') %>%
    summarise(all_correct = all(correct), .groups = "drop") %>%
    pull(all_correct)

  return(c(
    comp1_1Correct = comp1[1],
    comp1_2Correct = comp1[2],
    comp2Correct = comp2,
    compCorrect = ifelse(sum(c(!comp1[1], !comp1[2], !comp2), na.rm = TRUE)>1, FALSE,TRUE)
  ))
}

correct_df <- map_dfr(full$prolific_pid, getComprehensionPass)
full <- bind_cols(full, correct_df)

cat('How many participants failed the first round of comprehension 1?\n',
full %>%
  filter(!comp1_1Correct) %>%
  distinct(prolific_pid) %>%
  nrow()
 , '\n')

cat('How many of those then failed the second round of comprehension 1?\n',
# if participants do not fail the first round they do not do the second round
full %>%
  filter(!comp1_2Correct) %>%
  distinct(prolific_pid) %>%
  nrow()
 , '\n')

cat('How many participants failed comprehension 2?\n',
full %>%
  filter(!comp2Correct) %>%
  distinct(prolific_pid) %>%
  nrow()
  , '\n')
```

```{r}
# remove participants who failed the comprehension checks
filtered <- full %>%
  filter(compCorrect)

cat('final sample after exclusion: N=',
filtered %>%
  distinct(prolific_pid) %>%
  nrow()
,'\n')
```
## Processing

```{r}
# focus on critical trials
df_speaker <- filtered %>%
  filter(trial_type == 'critical-speaker') %>%
  select(where(~!all(is.na(.))))

df_speaker_key_trials <- df_speaker %>%
  filter(left_marble == 'blue' & right_marble == 'red')


# long-form dataframe, data are recoded using the response_map column to columns capturing:
# - prescriptive normality for the given religion
# - religion against which the participants judged the utterances
# - cause recoded as colour of the ball instead of left right

df_speaker_key_trials <- df_speaker_key_trials %>%
  pivot_longer(
    cols = c(response_relig_1_left, response_relig_1_right, response_relig_2_left, response_relig_2_right),
    names_to = 'response_map',
    values_to = 'speaker_likelihood'
  ) %>%
  mutate(presc_normality = ifelse(response_map == "response_relig_1_left" | response_map == "response_relig_2_right", 'normal', 'abnormal')) %>%
  mutate(religion = ifelse(grepl('relig_1', response_map), 'Rel 1 (red bad)', 'Rel 2 (blue bad)')) %>%
  mutate(cause = ifelse(grepl('left', response_map), 'blue', 'red'))

# focus on critical trials
df_listener <- filtered %>%
  filter(trial_type == 'critical-listener') %>%
  select(where(~!all(is.na(.))))

# recode responses so that responses about each possible cause can be plotted in one range
df_listener_key_trials <- df_listener %>%
  filter(left_marble == 'blue' & right_marble == 'red') %>%
  mutate(response = ifelse(actual_outcome == 'right', 8 - as.numeric(response_relig_unk),
                           as.numeric(response_relig_unk)))

```
With data processed, we can check how many data points for which condition.
```{r}
# There are 2(mechanism) x 3 (effect valence) x 2 (presc normality) = 12 conditions
df_speaker_key_trials %>%
  count(mechanism, effect_valence, presc_normality) %>%
  kable(format = 'markdown')

# There are 2(mechanism) x 3(effect valence) = 6 conditions
df_listener_key_trials %>%
  count(mechanism, effect_valence) %>%
  kable(format = 'markdown')
```

## Generate hypothetical simulated data
```{r}

# Generate n sample data points for a given condition from a normal distribution for a given mean and sd
get_speaker_samples <- function(normality, mechanism, valence, mean, sd, size = 50){
  scale <- 1:7
  probs <- dnorm(scale, mean = mean, sd = sd)
  probs <- probs / sum(probs)
  df <- data.frame(
    speaker_likelihood = sample(scale, size = size, replace = TRUE, prob = probs),
    presc_normality = rep(normality, size),
    effect_valence = rep(valence, size),
    mechanism = rep(mechanism, size)
  )
  return(df)
}

# Generate n sample data points for a given condition from a normal distribution for a given mean and sd
get_listener_samples <- function(mechanism, valence, mean, sd, size = 50) {
  scale <- 1:7
  probs <- dnorm(scale, mean = mean, sd = sd)
  probs <- probs / sum(probs)
  df <- data.frame(
    response_relig_unk = sample(scale, size = size, replace = TRUE, prob = probs),
    effect_valence = rep(valence, size),
    mechanism = rep(mechanism, size)
  )
  return(df)
}
```

```{r}
# get table of means and sds for each condition based on which full dataset is simulated
speaker_conditions <- read.csv(here("01-experiments","03-phase-speaker-and-listener-oriented","01-exp-prescrNorm-speakerListener","02 analysis","speaker-conditions_pilot-01.csv"), stringsAsFactors = FALSE)
listener_conditions <- read.csv(here("01-experiments","03-phase-speaker-and-listener-oriented","01-exp-prescrNorm-speakerListener","02 analysis","listener-conditions_pilot-01.csv"), stringsAsFactors = FALSE)

set.seed(148982)
# generate n datapoints for each condition for the speaker task
df_pred_speaker_trials <- do.call(rbind, apply(speaker_conditions, 1, function(row) {
  get_speaker_samples(row["normality"], row["mechanism"], row["valence"], as.numeric(row["mean"]), as.numeric(row["sd"]))
}))

# generate n datapoints for each condition for the listener task
df_pred_listener_trials <- do.call(rbind, apply(listener_conditions, 1, function(row) {
  get_listener_samples(row["mechanism"], row["valence"], as.numeric(row["mean"]), as.numeric(row["sd"]))
}))
```

## Data Visualisation

### Speaker task
```{r}
#| echo: true
#| warning: false
dodgewidth <- .3

plot_speaker <- function(speaker_trials) {
  plot <- speaker_trials %>%
    ggplot(aes(x = presc_normality, y = speaker_likelihood, color = effect_valence, shape = effect_valence)) +
    geom_jitter(aes(shape = effect_valence), position = position_jitterdodge(jitter.width = 0.05, jitter.height = .4, dodge.width = dodgewidth), alpha = .4) +
    scale_color_manual(values = c("unpleasant" = project_colors[2], "neutral" = project_colors[1], "pleasant" = project_colors[3])) +
    facet_grid(. ~ mechanism) +
    stat_summary(fun = 'mean', position = position_dodge(width = dodgewidth)) +
    stat_summary(fun.data = 'mean_se', position = position_dodge(width = dodgewidth)) +
    stat_summary(fun = 'mean', geom = 'line', aes(group = effect_valence),
                 position = position_dodge(width = dodgewidth)) +
    scale_y_continuous(breaks = 1:7) +
    coord_cartesian(ylim = c(1, 7)) +
    geom_hline(aes(yintercept = 4), linetype = 'dashed') +
    ylab('Assigned likelihood that the speaker would say this') +
    xlab('Prescriptive normality') +
    theme_classic()
  return(plot)
}

exp1_speaker <- plot_speaker(df_speaker_key_trials)
exp1_speaker

exp1_pred_speaker <- (plot_speaker(df_pred_speaker_trials))
exp1_pred_speaker

(exp1_speaker | exp1_pred_speaker) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom")
```
### Listener Task
```{r}
#| echo: true
#| warning: false
plot_listener <- function(listener_trials) {
  plot <- listener_trials %>%
    ggplot(aes(x = mechanism, y = response_relig_unk, color = effect_valence, shape = effect_valence)) +
    geom_jitter(aes(shape = effect_valence), position = position_jitterdodge(jitter.width = 0.05, jitter.height = .2, dodge.width = dodgewidth), alpha = .4) +
    scale_color_manual(values = c("unpleasant" = project_colors[2], "neutral" = project_colors[1], "pleasant" = project_colors[3])) +
    stat_summary(fun = 'mean', position = position_dodge(width = dodgewidth)) +
    stat_summary(fun.data = 'mean_se', position = position_dodge(width = dodgewidth)) +
    stat_summary(fun = 'mean', geom = 'line', aes(group = effect_valence),
                 position = position_dodge(width = dodgewidth)) +
    scale_y_continuous(breaks = 1:7) +
    coord_cartesian(ylim = c(1, 7)) +
    geom_hline(aes(yintercept = 4), linetype = 'dashed') +
    ylab('Inference that cause is (prescriptive) norm-violating') +
    xlab('Mechanism') +
    theme_classic()
  return(plot)
}

exp1_listener <- plot_listener(df_listener_key_trials)
exp1_listener

exp1_pred_listener <- (plot_listener(df_pred_listener_trials))
exp1_pred_listener

(exp1_listener | exp1_pred_listener) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom")
```

