---
title: "Data Exploration - Exp 1, Exp 2, and Exp 3"
format:
  html:
    toc: true
    # toc-location: left
    toc-depth: 12
    code-fold: true
execute:
  fig-width: 8
---

This notebook contains an exploratory analysis of three experiments in the CausalAttribInference project. Collected human data from pilots is looked at through the lens of the following set of hypotheses.

## Preprocessing

First, we clean up the data by renaming columns and removing empty rows. We start preparing for data exclusion by logging correctness of all comprehension responses.

```{r preprocessing}
#| code-summary: "Preprocessing"
#| warning: false
library(tidyverse)
library(ggbeeswarm)
library(ggbrace)
library(GGally)
library(patchwork)
library(cowplot)
library(cspplot)
library(brms)
library(tidybayes)
library(BayesFactor)
library(aida)
library(faintr)
library(tidyboot)
library(tidyjson)
library(here)
library(knitr)

##################################################

# these options help Stan run faster
options(mc.cores = parallel::detectCores(), brms.backend = "cmdstanr")

# use the CSP-theme for plotting
theme_set(theme_csp())

# global color scheme from CSP
project_colors <- cspplot::list_colors() |> pull(hex)

# setting theme colors globally
scale_colour_discrete <- function(...) {
  scale_colour_manual(..., values = project_colors)
}

scale_fill_discrete <- function(...) {
  scale_fill_manual(..., values = project_colors)
}

##################################################

set.seed(148982)

exp1_raw <- as_tibble(read.csv(here(
  "01-experiments",
  "03-phase-speaker-and-listener-oriented",
  "01-exp-prescrNorm-speakerListener",
  "01 data",
  "results_pilot-01.csv"
)))
exp2_raw <- as_tibble(read.csv(here(
  "01-experiments",
  "03-phase-speaker-and-listener-oriented",
  "02-exp-statisNorm-speakerListener",
  "01 data",
  "results_pilot-01.csv"
)))
exp3_raw <- as_tibble(read.csv(here(
  "01-experiments",
  "03-phase-speaker-and-listener-oriented",
  "03-exp-prescrStatisNorm-speakerListener",
  "01 data",
  "results_pilot-01.csv"
)))

exp1_full <- exp1_raw |>
  rename(trial_type = trialType) |>
  rename(trial_nr = trialNr) |>
  select(where(~ !all(is.na(.)))) |>
  mutate(
    correct = ifelse(
      is.na(correct_response),
      TRUE,
      correct_response == response
    )
  )

exp2_full <- exp2_raw |>
  rename(trial_type = trialType) |>
  rename(trial_nr = trialNr) |>
  select(where(~ !all(is.na(.)))) |>
  mutate(
    correct = ifelse(
      is.na(correct_response),
      TRUE,
      correct_response == response
    ),
    correct_awareness = ifelse(
      is.na(correct_response_awareness),
      TRUE,
      correct_response_awareness == response_awareness
    ),
    correct_control = ifelse(
      is.na(correct_response_control),
      TRUE,
      correct_response_control == response_control
    ),
    correct_bg = ifelse(
      is.na(correct_response_bg),
      TRUE,
      correct_response_bg == response_bg
    ),
    correct_yr = ifelse(
      is.na(correct_response_yr),
      TRUE,
      correct_response_yr == response_yr
    ),
    correct_unlabeled = ifelse(
      is.na(correct_response_unlabeled),
      TRUE,
      correct_response_unlabeled == response_unlabeled
    )
  ) |>
  group_by(prolific_pid) |>
  mutate(
    correct_bg = all(correct_bg),
    correct_awareness = all(correct_awareness),
    correct_control = all(correct_control),
    correct_bg = all(correct_bg),
    correct_yr = all(correct_yr),
    correct_unlabeled = all(correct_unlabeled),
  ) |>
  ungroup()

exp3_full <- exp3_raw |>
  rename(trial_type = trialType) |>
  rename(trial_nr = trialNr) |>
  mutate(
    response = if_else(
      !is.na(correct_response_bias),
      correct_response_bias,
      response
    )
  ) |>
  select(-correct_response_bias) |>
  select(where(~ !all(is.na(.)))) |>
  mutate(
    correct = ifelse(
      is.na(correct_response),
      TRUE,
      correct_response == response
    )
  )
```

## Exclusion

We exclude from further analysis participants who didn't pass the first set of comprehension questions even on their second attempt or failed more than one question from the second set of comprehension questions.

<details>
<summary>See tabular overviews</summary>

```{r exclusion}

exp1_getComprehensionPass <- function(id) {
  participant <- exp1_full |> filter(prolific_pid == id)
  comp1 <- participant |>
    filter(trial_type %in% c("comprehension-1-1", "comprehension-1-2")) |>
    group_by(trial_type) |>
    summarise(all_correct = all(correct), .groups = "drop") |>
    arrange(trial_type) |>
    pull(all_correct)

  comp2 <- participant |>
    filter(trial_type == 'comprehension-2') |>
    summarise(all_correct = all(correct), .groups = "drop") |>
    pull(all_correct)

  return(c(
    comp1_1Correct = comp1[1],
    comp1_2Correct = comp1[2],
    comp2Correct = comp2,
    compCorrect = ifelse(
      sum(c(!comp1[1], !comp1[2], !comp2), na.rm = TRUE) > 1,
      FALSE,
      TRUE
    )
  ))
}

exp2_getComprehensionPass <- function(id) {
  participant <- exp2_full |> filter(prolific_pid == id)
  comp1 <- participant |>
    filter(trial_type %in% c("comprehension-1-1", "comprehension-1-2")) |>
    group_by(trial_type) |>
    summarise(all_correct = all(correct), .groups = "drop") |>
    arrange(trial_type) |>
    pull(all_correct)

  return(c(
    comp1_1Correct = comp1[1],
    comp1_2Correct = comp1[2],
    compCorrect = ifelse(
      sum(
        c(
          !comp1[1],
          !comp1[2],
          !all(participant$correct_awareness),
          !all(participant$correct_control),
          !all(participant$correct_bg),
          !all(participant$correct_yr),
          !all(participant$correct_unlabeled)
        ),
        na.rm = TRUE
      ) >
        1,
      FALSE,
      TRUE
    )
  ))
}

exp3_getComprehensionPass <- function(id) {
  participant <- exp3_full |> filter(prolific_pid == id)

  comp1 <- participant |>
    filter(trial_type %in% c("comprehension-1-1", "comprehension-1-2")) |>
    group_by(trial_type) |>
    summarise(all_correct = all(correct), .groups = "drop") |>
    arrange(trial_type) |>
    pull(all_correct)

  comp2 <- participant |>
    filter(trial_type == 'comprehension-2') |>
    summarise(all_correct = all(correct), .groups = "drop") |>
    pull(all_correct)

  comp3 <- participant |>
    filter(trial_type == 'comprehension-3') |>
    summarise(all_correct = all(correct), .groups = "drop") |>
    pull(all_correct)

  return(c(
    comp1_1Correct = comp1[1],
    comp1_2Correct = comp1[2],
    comp2Correct = comp2,
    comp3Correct = comp3,
    compCorrect = ifelse(
      sum(
        c(
          !comp1[1],
          !comp1[2],
          !comp2,
          !comp3
        ),
        na.rm = TRUE
      ) >
        1,
      FALSE,
      TRUE
    )
  ))
}

exp1_full <- bind_cols(
  exp1_full,
  map_dfr(exp1_full$prolific_pid, exp1_getComprehensionPass)
)
exp2_full <- bind_cols(
  exp2_full,
  map_dfr(exp2_full$prolific_pid, exp2_getComprehensionPass)
)
exp3_full <- bind_cols(
  exp3_full,
  map_dfr(exp3_full$prolific_pid, exp3_getComprehensionPass)
)


# helper to count distinct participants matching a condition
n_pids <- function(df) df |> distinct(prolific_pid) |> nrow()

tibble(
  Step = c(
    "Collected sample",
    "Failed comprehension 1 (only round 1)",
    "Failed comprehension 1 (round 1 and 2)",
    "Failed comprehension 2",
    "Final sample after exclusion"
  ),
  n = c(
    exp1_full |> n_pids(),
    exp1_full |> filter(!comp1_1Correct) |> n_pids(),
    exp1_full |> filter(!comp1_2Correct) |> n_pids(),
    exp1_full |> filter(!comp2Correct) |> n_pids(),
    exp1_full |> filter(compCorrect) |> n_pids()
  )
) |>
  kable(caption = "Comprehension check exclusions (Exp 1)")


tibble(
  Step = c(
    "Collected sample",
    "Failed comprehension 1 (only round 1)",
    "Failed comprehension 1 (round 1 and 2)",
    "Failed comprehension 2: awareness",
    "Failed comprehension 2: control",
    "Failed comprehension 2: bg",
    "Failed comprehension 2: yr",
    "Failed comprehension 2: unlabeled",
    "Final sample after exclusion"
  ),
  n = c(
    exp2_full |> n_pids(),
    exp2_full |> filter(!comp1_1Correct) |> n_pids(),
    exp2_full |> filter(!comp1_2Correct) |> n_pids(),
    exp2_full |> filter(!correct_awareness) |> n_pids(),
    exp2_full |> filter(!correct_control) |> n_pids(),
    exp2_full |> filter(!correct_bg) |> n_pids(),
    exp2_full |> filter(!correct_yr) |> n_pids(),
    exp2_full |> filter(!correct_unlabeled) |> n_pids(),
    exp2_full |> filter(compCorrect) |> n_pids()
  )
) |>
  kable(caption = "Comprehension check exclusions (Exp 2)")


tibble(
  Step = c(
    "Collected sample",
    "Failed comprehension 1 (only round 1)",
    "Failed comprehension 1 (round 1 and 2)",
    "Failed comprehension 2",
    "Failed comprehension 3",
    "Final sample after exclusion"
  ),
  n = c(
    exp3_full |> n_pids(),
    exp3_full |> filter(!comp1_1Correct) |> n_pids(),
    exp3_full |> filter(!comp1_2Correct) |> n_pids(),
    exp3_full |> filter(!comp2Correct) |> n_pids(),
    exp3_full |> filter(!comp3Correct) |> n_pids(),
    exp3_full |> filter(compCorrect) |> n_pids()
  )
) |>
  kable(caption = "Comprehension check exclusions (Exp 3)")

exp1_filtered <- exp1_full |>
  filter(compCorrect)
exp2_filtered <- exp2_full |>
  filter(compCorrect)
exp3_filtered <- exp3_full |>
  filter(compCorrect)
```

```{r focus-critical-trials}

valence_levels <- c("pleasant", "neutral", "unpleasant")

factorise_valence <- function(df) {
  df$effect_valence <- factor(
    df$effect_valence,
    levels = valence_levels
  )
  df
}

exp1_filtered <- factorise_valence(exp1_filtered)
exp2_filtered <- factorise_valence(exp2_filtered)
exp3_filtered <- factorise_valence(exp3_filtered)

# Filter critical trials for speaker and listener tasks across all three Exps

# Exp1

# focus on critical trials
exp1_speaker <- exp1_filtered |>
  filter(trial_type == 'critical-speaker') |>
  select(where(~ !all(is.na(.))))

# long-form dataframe, data are recoded using the response_map column to columns capturing:
# - prescriptive normality for the given religion
# - religion against which the participants judged the utterances
# - cause recoded as colour of the ball instead of left right

exp1_speaker_key_trials <- exp1_speaker |>
  filter(left_marble == 'blue' & right_marble == 'red') |>
  pivot_longer(
    cols = c(
      response_relig_1_left,
      response_relig_1_right,
      response_relig_2_left,
      response_relig_2_right
    ),
    names_to = 'response_map',
    values_to = 'speaker_likelihood'
  ) |>
  mutate(
    presc_normality = ifelse(
      response_map == "response_relig_1_left" |
        response_map == "response_relig_2_right",
      'normal',
      'abnormal'
    )
  ) |>
  mutate(
    religion = ifelse(
      grepl('relig_1', response_map),
      'Rel 1 (red bad)',
      'Rel 2 (blue bad)'
    )
  ) |>
  mutate(cause = ifelse(grepl('left', response_map), 'blue', 'red'))

# focus on critical trials
exp1_listener <- exp1_filtered |>
  filter(trial_type == 'critical-listener') |>
  select(where(~ !all(is.na(.))))

# recode responses so that responses about each possible cause can be plotted in one range
exp1_listener_key_trials <- exp1_listener |>
  filter(left_marble == 'blue' & right_marble == 'red') |>
  mutate(
    response = ifelse(
      actual_outcome == 'right',
      8 - as.numeric(response_relig_unk),
      as.numeric(response_relig_unk)
    )
  )

# Exp2

exp2_speaker <- exp2_filtered |>
  filter(trial_type == 'critical-speaker') |>
  select(where(~ !all(is.na(.))))

exp2_speaker_key_trials <- exp2_speaker |>
  filter(left_marble == 'blue' & right_marble == 'red') |>
  pivot_longer(
    cols = c(response_left, response_right),
    names_to = 'response_map',
    values_to = 'speaker_likelihood'
  ) |>
  mutate(
    stat_normality = ifelse(
      response_map == 'response_left',
      ifelse(island_type == 'B-G', 'normal', 'abnormal'),
      ifelse(island_type == 'Y-R', 'normal', 'abnormal')
    )
  ) |>
  mutate(cause = ifelse(grepl('left', response_map), 'blue', 'red'))

exp2_listener <- exp2_filtered |>
  filter(trial_type == 'critical-listener') |>
  select(where(~ !all(is.na(.))))

exp2_listener_key_trials <- exp2_listener |>
  filter(left_marble == 'blue' & right_marble == 'red') |>
  mutate(
    response = ifelse(
      actual_outcome == 'right',
      8 - as.numeric(response_unk),
      as.numeric(response_unk)
    )
  )

#Exp3

exp3_speaker <- exp3_filtered |>
  filter(trial_type == 'critical-speaker') |>
  select(where(~ !all(is.na(.))))

exp3_speaker_key_trials <- exp3_speaker |>
  filter(left_marble == 'blue' & right_marble == 'red') |>
  pivot_longer(
    cols = c(
      response_relig_1_left,
      response_relig_1_right,
      response_relig_2_left,
      response_relig_2_right
    ),
    names_to = 'response_map',
    values_to = 'speaker_likelihood'
  ) |>
  mutate(
    presc_normality = ifelse(
      response_map == "response_relig_1_left" |
        response_map == "response_relig_2_right",
      'normal',
      'abnormal'
    )
  ) |>
  mutate(
    stat_normality = case_when(
      stat_norm == "blue" &
        grepl("left", response_map, ignore.case = TRUE) ~ "normal",
      stat_norm == "red" &
        grepl("right", response_map, ignore.case = TRUE) ~ "normal",
      TRUE ~ "abnormal"
    )
  ) |>
  mutate(
    religion = ifelse(
      grepl('relig_1', response_map),
      'Rel 1 (red bad)',
      'Rel 2 (blue bad)'
    )
  ) |>
  mutate(cause = ifelse(grepl('left', response_map), 'blue', 'red'))

exp3_listener <- exp3_filtered |>
  filter(trial_type == 'critical-listener') |>
  select(where(~ !all(is.na(.))))

exp3_listener_key_trials <- exp3_listener |>
  filter(left_marble == 'blue' & right_marble == 'red') |>
  mutate(
    response = ifelse(
      actual_outcome == 'right',
      8 - as.numeric(response_relig_unk),
      as.numeric(response_relig_unk)
    )
  ) |>
  mutate(
    stat_normality = case_when(
      stat_norm == "blue" & actual_outcome == 'left' ~ "normal",
      stat_norm == "red" & actual_outcome == 'right' ~ "normal",
      TRUE ~ "abnormal"
    )
  )
```

</details>

## Sample size per conditions

(In the speaker task, we get four data points per participant; in the listener task we get one data point.) The following tables show only conditions for which we have at least one value in the dataset.

<details>
<summary>See tabular overviews</summary>

```{r conditions-overview}
#| code-summary: "Overview of conditions"

exp1_speaker_key_trials |>
  count(mechanism, effect_valence, presc_normality) |>
  rowid_to_column(" ") |>
  kable(
    format = 'markdown',
    caption = "Exp1 (speaker): 2(mechanism) x 3 (effect valence) x 2 (presc normality) = 12 conditions"
  )
exp1_listener_key_trials |>
  count(mechanism, effect_valence) |>
  rowid_to_column(" ") |>
  kable(
    format = 'markdown',
    caption = "Exp1 (listener): 2(mechanism) x 3(effect valence) = 6 conditions"
  )

exp2_speaker_key_trials |>
  count(mechanism, effect_valence, stat_normality) |>
  rowid_to_column(" ") |>
  kable(
    format = 'markdown',
    caption = "Exp2 (speaker): 2(mechanism) x 3 (effect valence) x 2 (stat normality) = 12 conditions"
  )
exp2_listener_key_trials |>
  count(mechanism, effect_valence) |>
  rowid_to_column(" ") |>
  kable(
    format = 'markdown',
    caption = "Exp2 (listener): 2(mechanism) x 3(effect valence) = 6 conditions"
  )

exp3_speaker_key_trials |>
  count(mechanism, effect_valence, presc_normality, stat_normality) |>
  rowid_to_column(" ") |>
  kable(
    format = 'markdown',
    caption = "Exp3 (speaker): 2(mechanism) x 3 (effect valence) x 2 (presc normality) x 2 (stat normality) = 24 conditions"
  )

exp3_listener_key_trials |>
  count(mechanism, effect_valence, stat_normality) |>
  rowid_to_column(" ") |>
  kable(
    format = 'markdown',
    caption = "Exp3 (listener): 2(mechanism) x 3(effect valence)  x 2 (stat normality) = 12 conditions"
  )
```

</details>

## Hypotheses

1.  People take **prescriptive** norms into account (as described by the effects of abnormal inflation in conjunction and abnormal deflation in disjunction) when making causal selections, and as listeners, they infer **prescriptive** norms held by the speaker based on their causal selection.

[*Experiment 1*]

2.  People take **statistical** norms into account (as described by the effects of abnormal inflation in conjunction and abnormal deflation in disjunction) when making causal selections, and as listeners, they infer **statistical** norms held by the speaker based on their causal selection.\

[*Experiment 2*]

3.

- Current literature does not say much on the possible combination of effects different norms. Therefore we offer two hypotheses, one that is based on current literature and then a naive linear combination hypothesis.

current-literature hypothesis: $[SN+PN] < [SN+PA], [SA+PN], [SA+PA]$ in conjunction, and $[SN+PN] < [SN+PA], [SA+PN], [SA+PA]$

We could think of the situations where at least one normality is abnormal as basically variants of the first two experiments in cases where a vignette would actually contain another kind of norm that was not manipulated - with one abormal norm, we would expect inflation and deflation from the one abnormality. This hypothesis does not address what happens when both normalities are abnormal.

When both **statistical** and **prescriptive** norms are present, people's causal ratings vary monotonically with the combined statistical-prescriptive norms, taking both into account when making causal selections such that:

-   in **conjunction**, likelihood ratings **increase** monotonically due to effect of abnormal inflation: $$[SN+PN] < [SA+PN] < [SA+PA]$$ $$[SN+PN] < [SN+PA] < [SA+PA]$$
-   in **disjunction**, likelihood ratings **decreases** monotonically due to the effect of abnormal deflation: $$[SN+PN] > [SA+PN] > [SA+PA]$$ $$[SN+PN] > [SN+PA] > [SA+PA]$$
*(SA - statistically abnormal, SN - statistically normal, PA - prescriptively abnormal, PN - prescriptively normal)*</br></br>
[!TODO] When both **statistical** and **prescriptive** norms are present, listeners infer **prescriptive** norms from the speaker's causal selection, and this inference is unaffected by knowledge of the statistical normality of the selected cause.

[*Experiment 3*]

4.  People take outcome valence into account when making causal selections, and as listeners, they infer the normality of the selected cause from it.

- Speakers select between the abnormal and normal cause based on outcome valence, in correspondence with the ordering unpleasant > neutral > pleasant:
  - **unpleasant** outcomes make speakers more likely to select the abnormal cause, less likely the normal;
  - **pleasant** outcomes make speakers more likely to select the normal cause, less likely the abnormal;
  - **neutral** outcomes do not steer selection either way, falling between the two.
- Listeners infer the (statistical/prescriptive) normality of the selected cause accordingly:
  - **unpleasant** outcomes make listeners more likely to infer the abnormal cause, less likely the normal;
  - **pleasant** outcomes make listeners more likely to infer the normal cause, less likely the abnormal;
  - **neutral** outcomes do not steer inference either way.

[*Experiment 1, Experiment 2, and Experiment 3*]

5.  [!TODO] Based on existing literature, we hypothesise that there is no effect of outcome valence (meaning that re-checking previous hypotheses stratified by outcome valence would not make a difference)

[*Experiment 1, Experiment 2, and Experiment 3*]

## Data Visualisation

### Hypothesis 1

#### Speaker

`utterance_likelihood ~ presc_normality * mechanism`

We expect:

- **H1:P1**: abnormal inflation in conjunction in speaker
- **H1:P2**: abnormal deflation in disjunction in speaker

```{r hyp1-speaker}
#| fig-cap: "E: 'The machine made sound A.' C: 'A [COLOUR] marble was released.' Colour ([COLOUR] = red or blue) is counterbalanced with the norm manipulation: assignment of the normal and abnormal condition to each colour is randomised across participants."

dodgewidth <- .3

fictional_transparency <- annotate(
  "rect",
  xmin = -Inf,
  xmax = Inf,
  ymin = -Inf,
  ymax = Inf,
  fill = "white",
  alpha = .3
)


exp1_speaker_params <- expand_grid(
  presc_normality = c("normal", "abnormal"),
  mechanism = c("conjunctive", "disjunctive"),
  effect_valence = c("pleasant", "neutral", "unpleasant")
) |>
  mutate(response = 4, sd = 1) |>
  mutate(
    response = response +
      case_when(
        # abnormal inflation and deflation effects
        presc_normality == 'abnormal' & mechanism == 'conjunctive' ~ 1,
        presc_normality == 'abnormal' & mechanism == 'disjunctive' ~ -1,
        .default = 0
      )
  ) |>
  mutate(
    response = response +
      case_when(
        # valence effects
        presc_normality == 'normal' & effect_valence == 'pleasant' ~ 1.5,
        presc_normality == 'normal' & effect_valence == 'unpleasant' ~ -1.5,
        presc_normality == 'abnormal' & effect_valence == 'pleasant' ~ -1.5,
        presc_normality == 'abnormal' & effect_valence == 'unpleasant' ~ 1.5,
        .default = 0
      )
  ) |>
  factorise_valence()

hyp1_speaker <- exp1_speaker_key_trials |>
  ggplot(aes(x = mechanism, y = speaker_likelihood, fill = presc_normality)) +
  stat_summary(
    fun = mean,
    geom = "col",
    width = 0.7,
    position = position_dodge(width = 0.7)
  ) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    width = 0.2,
    position = position_dodge(width = 0.7)
  ) +
  scale_fill_manual(values = c(CSP_colors[2], CSP_colors[4])) +
  scale_y_continuous(breaks = 1:7) +
  coord_cartesian(ylim = c(1, 7)) +
  geom_hline(aes(yintercept = 4), linetype = 'dashed') +
  labs(
    x = 'Causal mechanism',
    y = "Likelihood rating: 'E because C'",
    fill = 'Prescriptive normality of C'
  ) +
  theme_minimal()

inflation_mean <- exp1_speaker_params |>
  filter(mechanism == "conjunctive" & presc_normality == "abnormal") |>
  pull(response) |>
  mean()
deflation_mean <- exp1_speaker_params |>
  filter(mechanism == "disjunctive" & presc_normality == "abnormal") |>
  pull(response) |>
  mean()

hyp1_pred_speaker <- exp1_speaker_params |>
  ggplot(aes(x = mechanism, y = response, fill = presc_normality)) +
  stat_summary(
    fun = mean,
    geom = "col",
    width = 0.7,
    position = position_dodge(width = 0.7)
  ) +
  scale_fill_manual(values = c(CSP_colors[2], "white")) +
  scale_y_continuous(breaks = 4) +
  coord_cartesian(ylim = c(1, 7)) +
  geom_hline(aes(yintercept = 4), linetype = 'dashed') +
  labs(
    x = 'Causal mechanism',
    y = "Likelihood rating: 'E because C'",
    fill = 'Prescriptive normality of C'
  ) +
  stat_brace(
    data = data.frame(x = c(0.98, 0.98), y = c(4, inflation_mean)),
    aes(x = x, y = y),
    width = 0.2,
    rotate = 90,
    inherit.aes = FALSE,
    colour = "black",
    linewidth = 0.7
  ) +
  annotate(
    "text",
    x = 1.35,
    y = (4 + inflation_mean) / 2,
    label = "H1:P1",
    fontface = "bold"
  ) +
  stat_brace(
    data = data.frame(x = c(1.98, 1.98), y = c(4, deflation_mean)),
    aes(x = x, y = y),
    width = 0.2,
    rotate = 90,
    inherit.aes = FALSE,
    colour = "black",
    linewidth = 0.7
  ) +
  annotate(
    "text",
    x = 2.35,
    y = (4 + deflation_mean) / 2,
    label = "H1:P2",
    fontface = "bold"
  ) +
  theme_minimal()

(hyp1_speaker +
  labs(title = "Collected") |
  hyp1_pred_speaker +
    labs(title = "Fictional") +
    fictional_transparency +
    guides(fill = "none")) +
  plot_layout(guides = "collect", axis_titles = "collect_y") &
  theme(legend.position = "bottom")
```

#### Listener

`presc_normality ~ mechanism`

We expect:

- **H1:P3**: Cause more likely to be prescriptively abnormal when mechanism is conjunctive
- **H1:P4**: Cause more likely to be prescriptively normal when mechanism is disjunctive

```{r hyp1-listener}
#| fig-cap: "Listener hears 'E because C' and infers whether C is prescriptively normal or abnormal."

exp1_listener_params <- expand_grid(
  mechanism = c("conjunctive", "disjunctive"),
  effect_valence = c("pleasant", "neutral", "unpleasant")
) |>
  mutate(response = 4, sd = 1) |>
  mutate(
    response = response +
      case_when(
        mechanism == "conjunctive" ~ 1,
        mechanism == "disjunctive" ~ -1
      )
  ) |>
  mutate(
    response = response +
      case_when(
        effect_valence == "pleasant" ~ -1.5,
        effect_valence == "unpleasant" ~ 1.5,
        .default = 0
      )
  ) |>
  factorise_valence()

hyp1_listener <- exp1_listener_key_trials |>
  ggplot(aes(x = mechanism, y = response)) +
  stat_summary(fun = mean, geom = "col", width = 0.7, fill = CSP_colors[5]) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  scale_y_continuous(breaks = 1:7) +
  coord_cartesian(ylim = c(1, 7)) +
  geom_hline(aes(yintercept = 4), linetype = 'dashed') +
  ylab('Inference that selected cause is prescriptively abnormal') +
  xlab('Causal mechanism') +
  theme_minimal()


inflation_mean <- exp1_listener_params |>
  filter(mechanism == "conjunctive") |>
  pull(response) |>
  mean()
deflation_mean <- exp1_listener_params |>
  filter(mechanism == "disjunctive") |>
  pull(response) |>
  mean()

hyp1_pred_listener <- exp1_listener_params |>
  ggplot(aes(x = mechanism, y = response)) +
  stat_summary(fun = mean, geom = "col", width = 0.7, fill = CSP_colors[5]) +
  scale_y_continuous(breaks = 4) +
  coord_cartesian(ylim = c(1, 7)) +
  geom_hline(aes(yintercept = 4), linetype = 'dashed') +
  ylab('Inference that selected cause is prescriptively abnormal') +
  xlab('Causal mechanism') +
  stat_brace(
    data = data.frame(x = c(1.33, 1.33), y = c(4, inflation_mean)),
    aes(x = x, y = y),
    width = 0.2,
    rotate = 90,
    inherit.aes = FALSE,
    colour = "black",
    linewidth = 0.7
  ) +
  annotate(
    "text",
    x = 1.73,
    y = (4 + inflation_mean) / 2,
    label = "H1:P3",
    fontface = "bold"
  ) +
  scale_x_discrete(expand = expansion(add = c(0.6, 1))) +
  stat_brace(
    data = data.frame(x = c(2.33, 2.33), y = c(4, deflation_mean)),
    aes(x = x, y = y),
    width = 0.2,
    rotate = 90,
    inherit.aes = FALSE,
    colour = "black",
    linewidth = 0.7
  ) +
  annotate(
    "text",
    x = 2.73,
    y = (4 + deflation_mean) / 2,
    label = "H1:P4",
    fontface = "bold"
  ) +
  theme_minimal()


(hyp1_listener +
  labs(title = "Collected") |
  hyp1_pred_listener + labs(title = "Fictional") + fictional_transparency) +
  plot_layout(guides = "collect", axis_titles = "collect_y") &
  theme(legend.position = "bottom")
```

### Hypothesis 2

##### Speaker

`utterance_likelihood ~ stat_normality * mechanism`

We expect:

- **H2:P1**: abnormal inflation in conjunction
- **H2:P2**: abnormal deflation in disjunction

```{r hyp2-speaker}
#| fig-cap: "E: 'The machine made sound A.' C: 'A [COLOUR] marble was released.' Colour ([COLOUR] = red or blue) is counterbalanced with the norm manipulation: assignment of the normal and abnormal condition to each colour is randomised across participants."

#   if (valence_facet) {
#     plot <- plot + facet_grid(effect_valence ~ .)
#   }
#   return(plot)
# }

exp2_speaker_params <- expand_grid(
  stat_normality = c("normal", "abnormal"),
  mechanism = c("conjunctive", "disjunctive"),
  effect_valence = c("pleasant", "neutral", "unpleasant")
) |>
  mutate(response = 4, sd = 1) |>
  mutate(
    response = response +
      case_when(
        # abnormal inflation and deflation effects
        stat_normality == 'abnormal' & mechanism == 'conjunctive' ~ 1,
        stat_normality == 'abnormal' & mechanism == 'disjunctive' ~ -1,
        .default = 0
      )
  ) |>
  mutate(
    response = response +
      case_when(
        # valence effects
        stat_normality == 'normal' & effect_valence == 'pleasant' ~ 1.5,
        stat_normality == 'normal' & effect_valence == 'unpleasant' ~ -1.5,
        stat_normality == 'abnormal' & effect_valence == 'pleasant' ~ -1.5,
        stat_normality == 'abnormal' & effect_valence == 'unpleasant' ~ 1.5,
        .default = 0
      )
  ) |>
  factorise_valence()

hyp2_speaker <- exp2_speaker_key_trials |>
  ggplot(aes(x = mechanism, y = speaker_likelihood, fill = stat_normality)) +
  stat_summary(
    fun = mean,
    geom = "col",
    width = 0.7,
    position = position_dodge(width = 0.7)
  ) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    width = 0.2,
    position = position_dodge(width = 0.7)
  ) +
  scale_fill_manual(values = c(CSP_colors[2], CSP_colors[4])) +
  scale_y_continuous(breaks = 1:7) +
  coord_cartesian(ylim = c(1, 7)) +
  geom_hline(aes(yintercept = 4), linetype = 'dashed') +
  labs(
    x = 'Causal mechanism',
    y = "Likelihood rating: 'E because C'",
    fill = 'Statistical normality of C'
  ) +
  theme_minimal()

inflation_mean <- exp2_speaker_params |>
  filter(mechanism == "conjunctive" & stat_normality == "abnormal") |>
  pull(response) |>
  mean()
deflation_mean <- exp2_speaker_params |>
  filter(mechanism == "disjunctive" & stat_normality == "abnormal") |>
  pull(response) |>
  mean()

hyp2_pred_speaker <- exp2_speaker_params |>
  ggplot(aes(x = mechanism, y = response, fill = stat_normality)) +
  stat_summary(
    fun = mean,
    geom = "col",
    width = 0.7,
    position = position_dodge(width = 0.7)
  ) +
  scale_fill_manual(values = c(CSP_colors[2], "white")) +
  scale_y_continuous(breaks = 4) +
  coord_cartesian(ylim = c(1, 7)) +
  geom_hline(aes(yintercept = 4), linetype = 'dashed') +
  labs(
    x = 'Causal mechanism',
    y = "Likelihood rating: 'E because C'",
    fill = 'Statistical normality of C'
  ) +
  stat_brace(
    data = data.frame(x = c(0.98, 0.98), y = c(4, inflation_mean)),
    aes(x = x, y = y),
    width = 0.2,
    rotate = 90,
    inherit.aes = FALSE,
    colour = "black",
    linewidth = 0.7
  ) +
  annotate(
    "text",
    x = 1.35,
    y = (4 + inflation_mean) / 2,
    label = "H2:P1",
    fontface = "bold"
  ) +
  stat_brace(
    data = data.frame(x = c(1.98, 1.98), y = c(4, deflation_mean)),
    aes(x = x, y = y),
    width = 0.2,
    rotate = 90,
    inherit.aes = FALSE,
    colour = "black",
    linewidth = 0.7
  ) +
  annotate(
    "text",
    x = 2.35,
    y = (4 + deflation_mean) / 2,
    label = "H2:P2",
    fontface = "bold"
  ) +
  theme_minimal()

(hyp2_speaker +
  labs(title = "Collected") |
  hyp2_pred_speaker +
    labs(title = "Fictional") +
    fictional_transparency +
    guides(fill = "none")) +
  plot_layout(guides = "collect", axis_titles = "collect_y") &
  theme(legend.position = "bottom")
```

#### Listener

`stat_normality ~ mechanism`

We expect:

- **H2:P3**: Cause more likely to be statistically abnormal when mechanism is conjunctive
- **H2:P4**: Cause more likely to be statistically normal when mechanism is disjunctive

```{r hyp2-listener}
#| fig-cap: "Listener hears 'E because C' and infers whether C is statistically normal or abnormal."

exp2_listener_params <- expand_grid(
  mechanism = c("conjunctive", "disjunctive"),
  effect_valence = c("pleasant", "neutral", "unpleasant")
) |>
  mutate(response = 4, sd = 1) |>
  mutate(
    response = response +
      case_when(
        mechanism == "conjunctive" ~ 1,
        mechanism == "disjunctive" ~ -1
      )
  ) |>
  mutate(
    response = response +
      case_when(
        effect_valence == "pleasant" ~ -1.5,
        effect_valence == "unpleasant" ~ 1.5,
        .default = 0
      )
  ) |>
  factorise_valence()

hyp2_listener <- exp2_listener_key_trials |>
  ggplot(aes(x = mechanism, y = response)) +
  stat_summary(fun = mean, geom = "col", width = 0.7, fill = CSP_colors[5]) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  scale_y_continuous(breaks = 1:7) +
  coord_cartesian(ylim = c(1, 7)) +
  geom_hline(aes(yintercept = 4), linetype = 'dashed') +
  ylab('Inference that selected cause is statistically abnormal') +
  xlab('Causal mechanism') +
  theme_minimal()


inflation_mean <- exp2_listener_params |>
  filter(mechanism == "conjunctive") |>
  pull(response) |>
  mean()
deflation_mean <- exp2_listener_params |>
  filter(mechanism == "disjunctive") |>
  pull(response) |>
  mean()

hyp2_pred_listener <- exp2_listener_params |>
  ggplot(aes(x = mechanism, y = response)) +
  stat_summary(fun = mean, geom = "col", width = 0.7, fill = CSP_colors[5]) +
  scale_y_continuous(breaks = 4) +
  coord_cartesian(ylim = c(1, 7)) +
  geom_hline(aes(yintercept = 4), linetype = 'dashed') +
  ylab('Inference that selected cause is statistically abnormal') +
  xlab('Causal mechanism') +
  stat_brace(
    data = data.frame(x = c(1.34, 1.34), y = c(4, inflation_mean)),
    aes(x = x, y = y),
    width = 0.2,
    rotate = 90,
    inherit.aes = FALSE,
    colour = "black",
    linewidth = 0.7
  ) +
  annotate(
    "text",
    x = 1.74,
    y = (4 + inflation_mean) / 2,
    label = "H2:P3",
    fontface = "bold"
  ) +
  scale_x_discrete(expand = expansion(add = c(0.6, 1))) +
  stat_brace(
    data = data.frame(x = c(2.34, 2.34), y = c(4, deflation_mean)),
    aes(x = x, y = y),
    width = 0.2,
    rotate = 90,
    inherit.aes = FALSE,
    colour = "black",
    linewidth = 0.7
  ) +
  annotate(
    "text",
    x = 2.73,
    y = (4 + deflation_mean) / 2,
    label = "H2:P4",
    fontface = "bold"
  ) +
  theme_minimal()


(hyp2_listener +
  labs(title = "Collected") |
  hyp2_pred_listener + labs(title = "Fictional") + fictional_transparency) +
  plot_layout(guides = "collect", axis_titles = "collect_y") &
  theme(legend.position = "bottom")
```

### Hypothesis 3

#### Speaker

`utterance_likelihood ~ stat_normality * presc_normality * mechanism`

We expect:

based on current literature we expect:

- **H3:P1**: in conjunction, due to the abnormal inflation effect: $4 < [SA+PN]; 4 < [SN+PA], 4 < [SA+PA]$
- **H3:P2**: in disjuntion, due to the abnormal deflation effect: $4 > [SA+PN]; 4 > [SN+PA]; 4 > [SA+PA]$

assuming that the effect of abnormal inflation for both kind of norms is additive:

- **H3:P3**:
- **H3:P4**:
- **H3:P5**:
- **H3:P6**:
- in conjunction, due to the abnormal inflation effect: $4 < [SA+PN], [SN+PA] < [SA+PA]$
- in disjuntion, due to the abnormal deflation effect: $4 > [SA+PN], [SN+PA] > [SA+PA]$

```{r hyp3-speaker}
#| fig-height: 8
#| fig-cap: "SA - Statistically abnormal, SN - Statistically normal, PA - Prescriptively abnormal, PN - Prescriptively normal. E: 'The machine made sound A.' C: 'A [COLOUR] marble was released.' Colour ([COLOUR] = red or blue) is counterbalanced with the norm manipulation: assignment of the normal and abnormal condition to each colour is randomised across participants.  C is subject to both statistical and prescriptive norms."

exp3_speaker_params_1 <- expand_grid(
  presc_normality = c("normal", "abnormal"),
  stat_normality = c("normal", "abnormal"),
  mechanism = c("conjunctive", "disjunctive"),
  effect_valence = c("pleasant", "neutral", "unpleasant")
) |>
  mutate(response = 4, sd = 1) |>
  mutate(
    response = response +
      case_when(
        mechanism == "conjunctive" &
          presc_normality == "abnormal" &
          stat_normality == "abnormal" ~ 1,
        mechanism == "conjunctive" &
          presc_normality == "abnormal" &
          stat_normality == "normal" ~ 1,
        mechanism == "conjunctive" &
          presc_normality == "normal" &
          stat_normality == "abnormal" ~ 1,
        mechanism == "conjunctive" &
          presc_normality == "normal" &
          stat_normality == "normal" ~ 0,

        mechanism == "disjunctive" &
          presc_normality == "abnormal" &
          stat_normality == "abnormal" ~ -1,
        mechanism == "disjunctive" &
          presc_normality == "abnormal" &
          stat_normality == "normal" ~ -1,
        mechanism == "disjunctive" &
          presc_normality == "normal" &
          stat_normality == "abnormal" ~ -1,
        mechanism == "disjunctive" &
          presc_normality == "normal" &
          stat_normality == "normal" ~ 0,
        .default = 0
      )
  ) |>
  mutate(
    response = response +
      case_when(
        # valence effects
        (stat_normality == 'normal' & presc_normality == 'normal') &
          effect_valence == 'pleasant' ~ 1.5,
        (stat_normality == 'normal' & presc_normality == 'normal') &
          effect_valence == 'unpleasant' ~ -1.5,
        (stat_normality == 'abnormal' & presc_normality == 'abnormal') &
          effect_valence == 'pleasant' ~ -1.5,
        (stat_normality == 'abnormal' & presc_normality == 'abnormal') &
          effect_valence == 'unpleasant' ~ 1.5,
        .default = 0
      )
  ) |>
  factorise_valence()

hyp3_speaker <- exp3_speaker_key_trials |>
  ggplot(aes(
    x = interaction(stat_normality, presc_normality),
    y = speaker_likelihood,
    fill = interaction(stat_normality, presc_normality)
  )) +
  stat_summary(
    fun = mean,
    geom = "col",
    width = 0.7
  ) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    width = 0.2
  ) +
  scale_fill_manual(
    values = c(CSP_colors[2], CSP_colors[3], CSP_colors[1], CSP_colors[4]),
    labels = c(
      "SA\nPA",
      "SN\nPA",
      "SA\nPN",
      "SN\nPN"
    )
  ) +
  scale_x_discrete(
    labels = c(
      "SA\nPA",
      "SN\nPA",
      "SA\nPN",
      "SN\nPN"
    )
  ) +
  scale_y_continuous(breaks = 1:7) +
  coord_cartesian(ylim = c(1, 7)) +
  geom_hline(aes(yintercept = 4), linetype = "dashed") +
  labs(
    x = "",
    y = "Likelihood rating: 'E because C'",
    fill = "Statistical × Prescriptive normality"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  facet_grid(. ~ mechanism) +
  theme_minimal()


inflation_mean <- exp3_speaker_params_1 |>
  filter(
    mechanism == "conjunctive" &
      stat_normality == "abnormal" &
      presc_normality == "abnormal"
  ) |>
  pull(response) |>
  mean()
deflation_mean <- exp3_speaker_params_1 |>
  filter(
    mechanism == "disjunctive" &
      stat_normality == "abnormal" &
      presc_normality == "abnormal"
  ) |>
  pull(response) |>
  mean()

hyp3_pred_speaker_1 <- exp3_speaker_params_1 |>
  ggplot(aes(
    x = interaction(stat_normality, presc_normality),
    y = response,
    fill = interaction(stat_normality, presc_normality)
  )) +
  stat_summary(
    fun = mean,
    geom = "col",
    width = 0.7
  ) +
  scale_fill_manual(
    values = c(CSP_colors[2], CSP_colors[3], CSP_colors[1], "white"),
    labels = c(
      "SA\nPA",
      "SN\nPA",
      "SA\nPN",
      ""
    )
  ) +
  scale_x_discrete(
    labels = c(
      "SA\nPA",
      "SN\nPA",
      "SA\nPN",
      ""
    ),
    expand = expansion(add = c(0.6, 1))
  ) +
  scale_y_continuous(breaks = 4) +
  coord_cartesian(ylim = c(1, 7)) +
  geom_hline(aes(yintercept = 4), linetype = "dashed") +
  labs(
    x = "",
    y = "Likelihood rating: 'E because C'",
    fill = "Statistical × Prescriptive normality"
  ) +
  geom_segment(
    data = data.frame(
      mechanism = c("conjunctive", "disjunctive"),
      x = c(0.6, 0.6),
      xend = c(3.5, 3.5),
      y = c(5, 3),
      yend = c(5, 3)
    ),
    aes(x = x, xend = xend, y = y, yend = yend),
    linetype = "dashed",
    colour = "black",
    inherit.aes = FALSE
  ) +
  facet_grid(. ~ mechanism) +
  # Brace 1 — conjunctive facet
  stat_brace(
    data = data.frame(
      mechanism = "conjunctive",
      x = c(3.5, 3.5),
      y = c(4, inflation_mean)
    ),
    aes(x = x, y = y),
    width = 0.2,
    rotate = 90,
    inherit.aes = FALSE,
    colour = "black",
    linewidth = 0.7
  ) +
  geom_text(
    data = data.frame(
      mechanism = "conjunctive",
      x = 4.4,
      y = (4 + inflation_mean) / 2,
      label = "H3:P1"
    ),
    aes(x = x, y = y, label = label),
    fontface = "bold",
    inherit.aes = FALSE
  ) +
  # Brace 2 — disjunctive facet
  stat_brace(
    data = data.frame(
      mechanism = "disjunctive",
      x = c(3.5, 3.5),
      y = c(4, deflation_mean)
    ),
    aes(x = x, y = y),
    width = 0.2,
    rotate = 90,
    inherit.aes = FALSE,
    colour = "black",
    linewidth = 0.7
  ) +
  geom_text(
    data = data.frame(
      mechanism = "disjunctive",
      x = 4.4,
      y = (4 + deflation_mean) / 2,
      label = "H3:P2"
    ),
    aes(x = x, y = y, label = label),
    fontface = "bold",
    inherit.aes = FALSE
  ) +
  theme_minimal()


exp3_speaker_params_2 <- expand_grid(
  presc_normality = c("normal", "abnormal"),
  stat_normality = c("normal", "abnormal"),
  mechanism = c("conjunctive", "disjunctive"),
  effect_valence = c("pleasant", "neutral", "unpleasant")
) |>
  mutate(response = 4, sd = 1) |>
  mutate(
    response = response +
      case_when(
        mechanism == "conjunctive" &
          presc_normality == "abnormal" &
          stat_normality == "abnormal" ~ 2,
        mechanism == "conjunctive" &
          presc_normality == "abnormal" &
          stat_normality == "normal" ~ 1,
        mechanism == "conjunctive" &
          presc_normality == "normal" &
          stat_normality == "abnormal" ~ 1,
        mechanism == "conjunctive" &
          presc_normality == "normal" &
          stat_normality == "normal" ~ 0,

        mechanism == "disjunctive" &
          presc_normality == "abnormal" &
          stat_normality == "abnormal" ~ -2,
        mechanism == "disjunctive" &
          presc_normality == "abnormal" &
          stat_normality == "normal" ~ -1,
        mechanism == "disjunctive" &
          presc_normality == "normal" &
          stat_normality == "abnormal" ~ -1,
        mechanism == "disjunctive" &
          presc_normality == "normal" &
          stat_normality == "normal" ~ 0,
        .default = 0
      )
  ) |>
  mutate(
    response = response +
      case_when(
        # valence effects
        (stat_normality == 'normal' & presc_normality == 'normal') &
          effect_valence == 'pleasant' ~ 1.5,
        (stat_normality == 'normal' & presc_normality == 'normal') &
          effect_valence == 'unpleasant' ~ -1.5,
        (stat_normality == 'abnormal' & presc_normality == 'abnormal') &
          effect_valence == 'pleasant' ~ -1.5,
        (stat_normality == 'abnormal' & presc_normality == 'abnormal') &
          effect_valence == 'unpleasant' ~ 1.5,
        .default = 0
      )
  ) |>
  factorise_valence()

inflation_mean_double_abnormal <- exp3_speaker_params_2 |>
  filter(
    mechanism == "conjunctive" &
      stat_normality == "abnormal" &
      presc_normality == "abnormal"
  ) |>
  pull(response) |>
  mean()
inflation_mean <- exp3_speaker_params_2 |>
  filter(
    mechanism == "conjunctive" &
      stat_normality == "abnormal" &
      presc_normality == "normal"
  ) |>
  pull(response) |>
  mean()

deflation_mean_double_abnormal <- exp3_speaker_params_2 |>
  filter(
    mechanism == "disjunctive" &
      stat_normality == "abnormal" &
      presc_normality == "abnormal"
  ) |>
  pull(response) |>
  mean()

deflation_mean <- exp3_speaker_params_2 |>
  filter(
    mechanism == "disjunctive" &
      stat_normality == "abnormal" &
      presc_normality == "normal"
  ) |>
  pull(response) |>
  mean()

hyp3_pred_speaker_2 <- exp3_speaker_params_2 |>
  ggplot(aes(
    x = interaction(stat_normality, presc_normality),
    y = response,
    fill = interaction(stat_normality, presc_normality)
  )) +
  stat_summary(
    fun = mean,
    geom = "col",
    width = 0.7
  ) +
  scale_fill_manual(
    values = c(CSP_colors[2], CSP_colors[3], CSP_colors[1], "white"),
    labels = c(
      "SA\nPA",
      "SN\nPA",
      "SA\nPN",
      ""
    )
  ) +
  scale_x_discrete(
    labels = c(
      "SA\nPA",
      "SN\nPA",
      "SA\nPN",
      ""
    ),
    expand = expansion(add = c(1.5, 1.3))
  ) +
  scale_y_continuous(breaks = 4) +
  coord_cartesian(ylim = c(1, 7)) +
  geom_hline(aes(yintercept = 4), linetype = "dashed") +
  labs(
    x = "",
    y = "Likelihood rating: 'E because C'",
    fill = "Statistical × Prescriptive normality"
  ) +
  geom_segment(
    data = data.frame(
      mechanism = c("conjunctive", "disjunctive"),
      x = c(1.5, 1.3),
      xend = c(3.5, 3.5),
      y = c(5, 3),
      yend = c(5, 3)
    ),
    aes(x = x, xend = xend, y = y, yend = yend),
    linetype = "dashed",
    colour = "black",
    inherit.aes = FALSE
  ) +
  geom_segment(
    data = data.frame(
      mechanism = c("conjunctive", "disjunctive"),
      x = c(0.5, 0.5),
      xend = c(2.5, 1.5),
      y = c(6, 2),
      yend = c(6, 2)
    ),
    aes(x = x, xend = xend, y = y, yend = yend),
    linetype = "dashed",
    colour = "black",
    inherit.aes = FALSE
  ) +
  facet_grid(. ~ mechanism) +
  # Brace 1 — conjunctive facet
  stat_brace(
    data = data.frame(
      mechanism = "conjunctive",
      x = c(3.5, 3.5),
      y = c(4, inflation_mean)
    ),
    aes(x = x, y = y),
    width = 0.2,
    rotate = 90,
    inherit.aes = FALSE,
    colour = "black",
    linewidth = 0.7
  ) +
  geom_text(
    data = data.frame(
      mechanism = "conjunctive",
      x = 4.6,
      y = (4 + inflation_mean) / 2,
      label = "H3:P3"
    ),
    aes(x = x, y = y, label = label),
    fontface = "bold",
    inherit.aes = FALSE
  ) +
  stat_brace(
    data = data.frame(
      mechanism = "conjunctive",
      x = c(2.5, 2.5),
      y = c(inflation_mean, inflation_mean_double_abnormal)
    ),
    aes(x = x, y = y),
    width = 0.2,
    rotate = 90,
    inherit.aes = FALSE,
    colour = "black",
    linewidth = 0.7
  ) +
  geom_text(
    data = data.frame(
      mechanism = "conjunctive",
      x = 3.6,
      y = (inflation_mean + inflation_mean_double_abnormal) / 2,
      label = "H3:P5"
    ),
    aes(x = x, y = y, label = label),
    fontface = "bold",
    inherit.aes = FALSE
  ) +
  # Brace 2 — disjunctive facet
  stat_brace(
    data = data.frame(
      mechanism = "disjunctive",
      x = c(3.5, 3.5),
      y = c(4, deflation_mean)
    ),
    aes(x = x, y = y),
    width = 0.2,
    rotate = 90,
    inherit.aes = FALSE,
    colour = "black",
    linewidth = 0.7
  ) +
  geom_text(
    data = data.frame(
      mechanism = "disjunctive",
      x = 4.6,
      y = (4 + deflation_mean) / 2,
      label = "H3:P4"
    ),
    aes(x = x, y = y, label = label),
    fontface = "bold",
    inherit.aes = FALSE
  ) +
  stat_brace(
    data = data.frame(
      mechanism = "disjunctive",
      x = c(1.3, 1.3),
      y = c(deflation_mean, deflation_mean_double_abnormal)
    ),
    aes(x = x, y = y),
    width = 0.2,
    rotate = 270,
    inherit.aes = FALSE,
    colour = "black",
    linewidth = 0.7
  ) +
  geom_text(
    data = data.frame(
      mechanism = "disjunctive",
      x = 0.2,
      y = (deflation_mean + deflation_mean_double_abnormal) / 2,
      label = "H3:P6"
    ),
    aes(x = x, y = y, label = label),
    fontface = "bold",
    inherit.aes = FALSE
  ) +
  theme_minimal()


(hyp3_speaker + labs(title = "Collected")) +
  (hyp3_pred_speaker_1 +
    labs(title = "Fictional (way 1)") +
    fictional_transparency +
    guides(fill = "none")) +
  (hyp3_pred_speaker_2 +
    labs(title = "Fictional (way 2)") +
    fictional_transparency +
    guides(fill = "none")) +
  plot_layout(
    design = "
          #B
          AB
          AC
          #C
      ",
    guides = "collect",
    axis_titles = "collect_y"
  ) &
  theme(legend.position = "bottom")
```


#### Listener

`presc_normality ~ stat_normality * mechanism`

Our listener inference task in Exp3 now is something that can give evidence for going against existing literature and in support of the linear combination version of hyp 3.

When we have statistical abnormality, we are focused on blue and red, between which we say speakers have no ordering in case 01. This would mean that a listener would not be able to use this for inference. Speakers likelihood rating would be inflated, but we can't say whether it was just due to the statistical abnormality or additionally due to prescriptive abnormality. We would expect both bars to be around 4.

- **H3:P7**: both conjunction and disjunction bars are at 4.

When we have statistical normality, we are focused on green and yellow, between which there is an ordering. This is basically the same case as before, we have statistically normal event and what changes is that there is an additional prescriptive abnormality. We would expect standard pattern of inflation in conjunction and deflation in disjunction.

- **H3:P8**: increased in conjunction
- **H3:P9**: decreased in disjunction


With statistical abnormality
This is where a hypothesis that includes some kind of linear combination of the two normalities would show. Comparing blue and red, we expect speakers to rate red higher, and so we would expect the same, but stronger, pattern of inflation and deflation.

- **H3:P10**: increase in conjunction
- **H3:P11**: decrease in disjunction

With statistical normality,
Here the situation is exactly the same as above because this variant of hyp3 does not change anything about the relationship between green and yellow.

- **H3:P8**: increased in conjunction
- **H3:P9**: decreased in disjunction

```{r hyp3-listener}
#| fig-height: 10
#| fig-cap: "With the knowledge of statistical norm held by the speaker, the listener hears 'E because C' and infers whether C is prescriptively normal or abnormal."

exp3_listener_params_1 <- expand_grid(
  stat_normality = c("normal", "abnormal"),
  mechanism = c("conjunctive", "disjunctive"),
  effect_valence = c("pleasant", "neutral", "unpleasant")
) |>
  mutate(response = 4, sd = 1) |>
  mutate(
    response = response +
      case_when(
        (stat_normality == "normal" & mechanism == "conjunctive") ~ 1,
        (stat_normality == "normal" & mechanism == "disjunctive") ~ -1,
        .default = 0
      )
  ) |>
  mutate(
    response = response +
      case_when(
        (stat_normality == 'normal') & effect_valence == 'pleasant' ~ 0,
        (stat_normality == 'normal') & effect_valence == 'unpleasant' ~ 0,
        (stat_normality == 'abnormal') & effect_valence == 'pleasant' ~ -1.5,
        (stat_normality == 'abnormal') & effect_valence == 'unpleasant' ~ 1.5,
        .default = 0
      )
  ) |>
  factorise_valence()

hyp3_listener <- exp3_listener_key_trials |>
  ggplot(aes(x = mechanism, y = response)) +
  stat_summary(fun = mean, geom = "col", width = 0.7, fill = CSP_colors[5]) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  scale_fill_manual(
    values = c(CSP_colors[2], CSP_colors[4])
  ) +
  scale_y_continuous(breaks = 1:7) +
  coord_cartesian(ylim = c(1, 7)) +
  geom_hline(aes(yintercept = 4), linetype = 'dashed') +
  labs(
    x = 'Causal mechanism',
    y = 'Inference that selected cause is prescriptively abnormal'
  ) +
  theme_minimal() +
  # if (valence_facet) {
  #   plot <- plot +
  #     facet_grid(
  #       effect_valence ~ stat_normality,
  #       labeller = labeller(
  #         stat_normality = c(
  #           normal = "Statistically normal",
  #           abnormal = "Statistically abnormal"
  #         )
  #       )
  #     )
  # } else {
  facet_grid(
    . ~ stat_normality,
    labeller = labeller(
      stat_normality = c(
        normal = "Statistically normal",
        abnormal = "Statistically abnormal"
      )
    )
  )

hyp3_pred_listener_1 <- exp3_listener_params_1 |>
  ggplot(aes(x = mechanism, y = response)) +
  stat_summary(fun = mean, geom = "col", width = 0.7, fill = CSP_colors[5]) +
  scale_fill_manual(
    values = c(CSP_colors[2], CSP_colors[4])
  ) +
  scale_y_continuous(breaks = 4) +
  coord_cartesian(ylim = c(1, 7)) +
  scale_x_discrete(expand = expansion(add = c(0, 1.3))) +
  geom_hline(aes(yintercept = 4), linetype = 'dashed') +
  labs(
    x = 'Causal mechanism',
    y = 'Inference that selected cause is prescriptively abnormal'
  ) +
  theme_minimal() +
  facet_grid(
    . ~ stat_normality,
    labeller = labeller(
      stat_normality = c(
        normal = "Statistically normal",
        abnormal = "Statistically abnormal"
      )
    )
  ) +
  geom_segment(
    data = data.frame(
      stat_normality = "abnormal",
      x = c(1, 2),
      xend = c(1.5, 1.5),
      y = c(4, 4),
      yend = c(5, 5)
    ),
    aes(x = x, xend = xend, y = y, yend = yend),
    linewidth = 0.7,
    colour = "black",
    inherit.aes = FALSE
  ) +
  geom_text(
    data = data.frame(
      stat_normality = "abnormal",
      x = 1.5 - 0.01,
      y = 5.15,
      label = "H3:P7"
    ),
    aes(x = x, y = y, label = label),
    fontface = "bold",
    inherit.aes = FALSE
  ) +
  stat_brace(
    data = data.frame(
      stat_normality = "normal",
      x = c(1.35, 1.35),
      y = c(4, inflation_mean)
    ),
    aes(x = x, y = y),
    width = 0.2,
    rotate = 90,
    inherit.aes = FALSE,
    colour = "black",
    linewidth = 0.7
  ) +
  geom_text(
    data = data.frame(
      stat_normality = "normal",
      x = 1.95,
      y = (4 + inflation_mean) / 2,
      label = "H3:P8"
    ),
    aes(x = x, y = y, label = label),
    fontface = "bold",
    inherit.aes = FALSE
  ) +
  stat_brace(
    data = data.frame(
      stat_normality = "normal",
      x = c(2.35, 2.35),
      y = c(deflation_mean, 4)
    ),
    aes(x = x, y = y),
    width = 0.2,
    rotate = 90,
    inherit.aes = FALSE,
    colour = "black",
    linewidth = 0.7
  ) +
  geom_text(
    data = data.frame(
      stat_normality = "normal",
      x = 2.95,
      y = (deflation_mean + 4) / 2,
      label = "H3:P9"
    ),
    aes(x = x, y = y, label = label),
    fontface = "bold",
    inherit.aes = FALSE
  )

exp3_listener_params_2 <- expand_grid(
  stat_normality = c("normal", "abnormal"),
  mechanism = c("conjunctive", "disjunctive"),
  effect_valence = c("pleasant", "neutral", "unpleasant")
) |>
  mutate(response = 4, sd = 1) |>
  mutate(
    response = response +
      case_when(
        effect_valence == "pleasant" ~ -1.5,
        effect_valence == "unpleasant" ~ 1.5,
        .default = 0
      )
  ) |>
  mutate(
    response = response +
      case_when(
        (stat_normality == "normal" & mechanism == "conjunctive") ~ 1,
        (stat_normality == "normal" & mechanism == "disjunctive") ~ -1,
        (stat_normality == "abnormal" & mechanism == "conjunctive") ~ 1,
        (stat_normality == "abnormal" & mechanism == "disjunctive") ~ -1,
        .default = 0
      )
  ) |>
  factorise_valence()

hyp3_pred_listener_2 <- exp3_listener_params_2 |>
  ggplot(aes(x = mechanism, y = response)) +
  stat_summary(fun = mean, geom = "col", width = 0.7, fill = CSP_colors[5]) +
  scale_fill_manual(
    values = c(CSP_colors[2], CSP_colors[4])
  ) +
  scale_y_continuous(breaks = 4) +
  coord_cartesian(ylim = c(1, 7)) +
  scale_x_discrete(expand = expansion(add = c(0, 1.5))) +
  geom_hline(aes(yintercept = 4), linetype = 'dashed') +
  labs(
    x = 'Causal mechanism',
    y = 'Inference that selected cause is prescriptively abnormal'
  ) +
  theme_minimal() +
  facet_grid(
    . ~ stat_normality,
    labeller = labeller(
      stat_normality = c(
        normal = "Statistically normal",
        abnormal = "Statistically abnormal"
      )
    )
  ) +
  stat_brace(
    data = data.frame(
      stat_normality = "normal",
      x = c(1.35, 1.35),
      y = c(4, inflation_mean)
    ),
    aes(x = x, y = y),
    width = 0.2,
    rotate = 90,
    inherit.aes = FALSE,
    colour = "black",
    linewidth = 0.7
  ) +
  geom_text(
    data = data.frame(
      stat_normality = "normal",
      x = 1.95,
      y = (4 + inflation_mean) / 2,
      label = "H3:P8"
    ),
    aes(x = x, y = y, label = label),
    fontface = "bold",
    inherit.aes = FALSE
  ) +
  stat_brace(
    data = data.frame(
      stat_normality = "normal",
      x = c(2.35, 2.35),
      y = c(deflation_mean, 4)
    ),
    aes(x = x, y = y),
    width = 0.2,
    rotate = 90,
    inherit.aes = FALSE,
    colour = "black",
    linewidth = 0.7
  ) +
  geom_text(
    data = data.frame(
      stat_normality = "normal",
      x = 2.95,
      y = (deflation_mean + 4) / 2,
      label = "H3:P9"
    ),
    aes(x = x, y = y, label = label),
    fontface = "bold",
    inherit.aes = FALSE
  ) +
  stat_brace(
    data = data.frame(
      stat_normality = "abnormal",
      x = c(1.35, 1.35),
      y = c(4, inflation_mean)
    ),
    aes(x = x, y = y),
    width = 0.2,
    rotate = 90,
    inherit.aes = FALSE,
    colour = "black",
    linewidth = 0.7
  ) +
  geom_text(
    data = data.frame(
      stat_normality = "abnormal",
      x = 2.05,
      y = (4 + inflation_mean) / 2,
      label = "H3:P10"
    ),
    aes(x = x, y = y, label = label),
    fontface = "bold",
    inherit.aes = FALSE
  ) +
  stat_brace(
    data = data.frame(
      stat_normality = "abnormal",
      x = c(2.35, 2.35),
      y = c(deflation_mean, 4)
    ),
    aes(x = x, y = y),
    width = 0.2,
    rotate = 90,
    inherit.aes = FALSE,
    colour = "black",
    linewidth = 0.7
  ) +
  geom_text(
    data = data.frame(
      stat_normality = "abnormal",
      x = 3.05,
      y = (deflation_mean + 4) / 2,
      label = "H3:P11"
    ),
    aes(x = x, y = y, label = label),
    fontface = "bold",
    inherit.aes = FALSE
  )

(hyp3_listener + labs(title = "Collected")) +
  (hyp3_pred_listener_1 +
    labs(title = "Fictional (way 1)") +
    fictional_transparency +
    guides(fill = "none")) +
  (hyp3_pred_listener_2 +
    labs(title = "Fictional (way 2)") +
    fictional_transparency +
    guides(fill = "none")) +
  plot_layout(
    design = "
          #B
          AB
          AC
          #C
      ",
    guides = "collect",
    axis_titles = "collect_y"
  ) &
  theme(legend.position = "bottom")
```

### Hypothesis 4

#### Speaker

`utterance_likelihood ~ presc_normality * effect_valence`\
`utterance_likelihood ~ stat_normality * effect_valence`

We expect:

- **H4:P1**: increase based on prescriptive/statistical normality due to pleasant
- **H4:P2**: decrease based on prescriptive/statistical abnormality due to pleasant
- **H4:P3**: no change based on prescriptive and/or statistical normality due to neutral
- **H4:P4**: increase based on prescriptive/statistical abnormality due to unpleasant
- **H4:P5**: decrease based on prescriptive/statistical normality due to unpleasant
- **H4:P6**: increase based on prescriptive and statistical normality due to pleasant
- **H4:P7**: decrease based on prescriptive and statistical abnormality due to pleasant
- **H4:P8**: increase based on prescriptive and statistical abnormality due to unpleasant
- **H4:P9**: decrease based on prescriptive and statistical normality due to unpleasant

For exp3 we can only really make claims about situation where both are either abnormal or normal. Since we don't know how them differing may or may not cancel out.

```{r hyp4-speaker}
#| fig-height: 10
#| fig-cap: "E: 'The machine made sound A.' C: 'A [COLOUR] marble was released.' Colour ([COLOUR] = red or blue) is counterbalanced with the norm manipulation: assignment of the normal and abnormal condition to each colour is randomised across participants. Data from Experiment 3 is collapsed over statistical normality of C, which was also manipulated in the experiment."

hyp4_plot_speaker <- function(speaker_trials, x, xlab) {
  plot <- speaker_trials |>
    ggplot(aes(x = {{ x }}, y = speaker_likelihood, fill = {{ x }})) +
    stat_summary(fun = mean, geom = "col", width = 0.7) +
    stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
    scale_y_continuous(breaks = 1:7) +
    coord_cartesian(ylim = c(1, 7)) +
    scale_fill_manual(
      values = c(
        "abnormal" = CSP_colors[2],
        "normal" = CSP_colors[4]
      )
    ) +
    geom_hline(aes(yintercept = 4), linetype = 'dashed') +
    ylab("Likelihood rating: 'E because C'") +
    xlab(xlab) +
    theme_minimal() +
    facet_grid(effect_valence ~ .)
  return(plot)
}

hyp4_plot_speaker_pred <- function(speaker_trials, x, xlab) {
  plot <- speaker_trials |>
    ggplot(aes(x = {{ x }}, y = response, fill = {{ x }})) +
    stat_summary(fun = mean, geom = "col", width = 0.7) +
    scale_y_continuous(breaks = 4) +
    coord_cartesian(ylim = c(1, 7)) +
    scale_fill_manual(
      values = c(
        "abnormal" = CSP_colors[2],
        "normal" = CSP_colors[4]
      )
    ) +
    scale_x_discrete(expand = expansion(add = c(1, 1))) +
    geom_hline(aes(yintercept = 4), linetype = 'dashed') +
    ylab("Likelihood rating: 'E because C'") +
    xlab(xlab) +
    theme_minimal() +
    facet_grid(effect_valence ~ .)
  return(plot)
}

ev_levels <- levels(exp1_speaker_params$effect_valence)

pred_1 <- list(
  stat_brace(
    data = data.frame(
      effect_valence = factor("pleasant", levels = ev_levels),
      x = c(2.33, 2.33),
      y = c(4, 5.5)
    ),
    aes(x = x, y = y),
    width = 0.2,
    rotate = 90,
    inherit.aes = FALSE,
    colour = "black",
    linewidth = 0.7
  ),
  geom_text(
    data = data.frame(
      effect_valence = factor("pleasant", levels = ev_levels),
      x = 2.78,
      y = (4 + 5.5) / 2,
      label = "H4:P1"
    ),
    aes(x = x, y = y, label = label),
    fontface = "bold",
    inherit.aes = FALSE
  ),
  stat_brace(
    data = data.frame(
      effect_valence = factor("pleasant", levels = ev_levels),
      x = c(0.68, 0.68),
      y = c(2.5, 4)
    ),
    aes(x = x, y = y),
    width = 0.12,
    rotate = 270,
    inherit.aes = FALSE,
    colour = "black",
    linewidth = 0.7
  ),
  geom_text(
    data = data.frame(
      effect_valence = factor("pleasant", levels = ev_levels),
      x = 0.3,
      y = (2.5 + 4) / 2,
      label = "H4:P2"
    ),
    aes(x = x, y = y, label = label),
    fontface = "bold",
    inherit.aes = FALSE
  )
)

pred_2 <- list(
  geom_segment(
    data = data.frame(
      effect_valence = factor("neutral", levels = ev_levels),
      x = c(1, 2),
      xend = c(1.5, 1.5),
      y = c(4, 4),
      yend = c(5, 5)
    ),
    aes(x = x, xend = xend, y = y, yend = yend),
    linewidth = 0.7,
    colour = "black",
    inherit.aes = FALSE
  ),
  geom_text(
    data = data.frame(
      effect_valence = factor("neutral", levels = ev_levels),
      x = 1.5 - 0.01,
      y = 5.45,
      label = "H4:P3"
    ),
    aes(x = x, y = y, label = label),
    fontface = "bold",
    inherit.aes = FALSE
  )
)

pred_3 <- list(
  stat_brace(
    data = data.frame(
      effect_valence = factor("unpleasant", levels = ev_levels),
      x = c(2.33, 2.33),
      y = c(2.5, 4)
    ),
    aes(x = x, y = y),
    width = 0.12,
    rotate = 90,
    inherit.aes = FALSE,
    colour = "black",
    linewidth = 0.7
  ),
  geom_text(
    data = data.frame(
      effect_valence = factor("unpleasant", levels = ev_levels),
      x = 2.78,
      y = (2.5 + 4) / 2,
      label = "H4:P5"
    ),
    aes(x = x, y = y, label = label),
    fontface = "bold",
    inherit.aes = FALSE
  ),
  stat_brace(
    data = data.frame(
      effect_valence = factor("unpleasant", levels = ev_levels),
      x = c(0.68, 0.68),
      y = c(4, 5.5)
    ),
    aes(x = x, y = y),
    width = 0.2,
    rotate = 270,
    inherit.aes = FALSE,
    colour = "black",
    linewidth = 0.7
  ),
  geom_text(
    data = data.frame(
      effect_valence = factor("unpleasant", levels = ev_levels),
      x = 0.3,
      y = (4 + 5.5) / 2,
      label = "H4:P4"
    ),
    aes(x = x, y = y, label = label),
    fontface = "bold",
    inherit.aes = FALSE
  )
)

hyp4_exp1_speaker <- hyp4_plot_speaker(
  exp1_speaker_key_trials,
  presc_normality,
  xlab = "Prescriptive normality of C"
)
hyp4_exp1_pred_speaker <- hyp4_plot_speaker_pred(
  exp1_speaker_params,
  presc_normality,
  xlab = "Prescriptive normality of C"
) +
  pred_1 +
  pred_2 +
  pred_3


hyp4_exp2_speaker <- hyp4_plot_speaker(
  exp2_speaker_key_trials,
  stat_normality,
  xlab = "Statistical normality of C"
)
hyp4_exp2_pred_speaker <- hyp4_plot_speaker_pred(
  exp2_speaker_params,
  stat_normality,
  xlab = "Statistical normality of C"
) +
  pred_1 +
  pred_2 +
  pred_3


((hyp4_exp1_speaker +
    labs(title = "Collected (Exp 1)")) +
   (hyp4_exp1_pred_speaker +
      labs(title = "Fictional (Exp 1)") +
      fictional_transparency) +
   (hyp4_exp2_speaker +
      labs(title = "Collected (Exp 2)") +
      guides(fill = "none")) +
   (hyp4_exp2_pred_speaker +
      labs(title = "Fictional (Exp 2)") +
      fictional_transparency +
      guides(fill = "none"))) +
  plot_layout(ncol = 2,
              guides = "collect",
              axes = "collect",
              axis_titles = "collect") &
  theme(legend.position = "bottom") &
  labs(fill = "(Prescriptive/Statistical) normality")
```



```{r hyp4-speaker-exp3}
#| fig-height: 10

hyp4_exp3_plot_speaker <- function(speaker_trials, xlab) {
  plot <- speaker_trials |>
    ggplot(aes(
      x = interaction(stat_normality, presc_normality),
      y = speaker_likelihood,
      fill = interaction(stat_normality, presc_normality)
    )) +
    stat_summary(fun = mean, geom = "col", width = 0.7) +
    stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
    scale_y_continuous(breaks = 1:7) +
    coord_cartesian(ylim = c(1, 7)) +
    scale_fill_manual(
      values = c(CSP_colors[2], CSP_colors[3], CSP_colors[1], CSP_colors[4])
    ) +
    geom_hline(aes(yintercept = 4), linetype = 'dashed') +
    ylab("Likelihood rating: 'E because C'") +
    xlab(xlab) +
    theme_minimal() +
    facet_grid(effect_valence ~ .)
  return(plot)
}

hyp4_exp3_plot_speaker_pred <- function(speaker_trials, xlab) {
  plot <- speaker_trials |>
    ggplot(aes(
      x = interaction(stat_normality, presc_normality),
      y = response,
      fill = interaction(stat_normality, presc_normality)
    )) +
    stat_summary(fun = mean, geom = "col", width = 0.7) +
    scale_y_continuous(breaks = 4) +
    coord_cartesian(ylim = c(1, 7)) +
    scale_fill_manual(
      values = c(CSP_colors[2], CSP_colors[3], CSP_colors[1], CSP_colors[4])
    ) +
    scale_x_discrete(
      expand = expansion(add = c(1.8, 1.8))
    ) +
    geom_hline(aes(yintercept = 4), linetype = 'dashed') +
    ylab("Likelihood rating: 'E because C'") +
    xlab(xlab) +
    theme_minimal() +
    facet_grid(effect_valence ~ .)
  return(plot)
}


hyp4_exp3_speaker <- hyp4_exp3_plot_speaker(
  exp3_speaker_key_trials,
  xlab = "Prescriptive normality of C"
)

hyp4_exp3_pred_speaker_1 <- hyp4_exp3_plot_speaker_pred(
  exp3_speaker_params_1 |> mutate(
      response = response +
      case_when(
            # just so we don't visualise what we don't make predictions about
        (stat_normality == "abnormal" & presc_normality == "normal" & effect_valence != "neutral") ~ -4,
        (stat_normality == "normal" & presc_normality == "abnormal" & effect_valence != "neutral") ~ -4,
        .default = 0
      )
  )
  ,
  xlab = "Prescriptive normality of C"
) +
  list(
    geom_segment(
      data = data.frame(
        effect_valence = factor("pleasant", levels = ev_levels),
        x = c(3.6, 0.6),
        xend = c(4.5, 1.4),
        y = c(5.5, 2.5),
        yend = c(5.5, 2.5)
      ),
      aes(x = x, xend = xend, y = y, yend = yend),
      linetype = "dashed",
      colour = "black",
      inherit.aes = FALSE
    ),
    stat_brace(
      data = data.frame(
        effect_valence = factor("pleasant", levels = ev_levels),
        x = c(4.5, 4.5),
        y = c(4, 5.5)
      ),
      aes(x = x, y = y),
      width = 0.2,
      rotate = 90,
      inherit.aes = FALSE,
      colour = "black",
      linewidth = 0.7
    ),
    geom_text(
      data = data.frame(
        effect_valence = factor("pleasant", levels = ev_levels),
        x = 5.2,
        y = (4 + 5.5) / 2,
        label = "H4:P6"
      ),
      aes(x = x, y = y, label = label),
      fontface = "bold",
      inherit.aes = FALSE
    ),
    stat_brace(
      data = data.frame(
        effect_valence = factor("pleasant", levels = ev_levels),
        x = c(0.7, 0.7),
        y = c(2.5, 4)
      ),
      aes(x = x, y = y),
      width = 0.2,
      rotate = 270,
      inherit.aes = FALSE,
      colour = "black",
      linewidth = 0.7
    ),
    geom_text(
      data = data.frame(
        effect_valence = factor("pleasant", levels = ev_levels),
        x = 0.01,
        y = (2.5 + 4) / 2,
        label = "H5:P7"
      ),
      aes(x = x, y = y, label = label),
      fontface = "bold",
      inherit.aes = FALSE
    )
  ) +
  list(
    geom_segment(
      data = data.frame(
        effect_valence = factor("neutral", levels = ev_levels),
        x = c(1, 2),
        xend = c(2.5, 2.5),
        y = c(4, 4),
        yend = c(5.5, 5.5)
      ),
      aes(x = x, xend = xend, y = y, yend = yend),
      linewidth = 0.7,
      colour = "black",
      inherit.aes = FALSE
    ),
    geom_segment(
      data = data.frame(
        effect_valence = factor("neutral", levels = ev_levels),
        x = c(3, 4),
        xend = c(2.5, 2.5),
        y = c(4, 4),
        yend = c(5.5, 5.5)
      ),
      aes(x = x, xend = xend, y = y, yend = yend),
      linewidth = 0.7,
      colour = "black",
      inherit.aes = FALSE
    ),
    geom_text(
      data = data.frame(
        effect_valence = factor("neutral", levels = ev_levels),
        x = 2.5,
        y = 5.8,
        label = "H4:P3"
      ),
      aes(x = x, y = y, label = label),
      fontface = "bold",
      inherit.aes = FALSE
    )
  ) +
  list(
    geom_segment(
      data = data.frame(
        effect_valence = factor("unpleasant", levels = ev_levels),
        x = c(3.6, 0.6),
        xend = c(4.5, 1.4),
        y = c(2.5, 5.5),
        yend = c(2.5, 5.5)
      ),
      aes(x = x, xend = xend, y = y, yend = yend),
      linetype = "dashed",
      colour = "black",
      inherit.aes = FALSE
    ),
    stat_brace(
      data = data.frame(
        effect_valence = factor("unpleasant", levels = ev_levels),
        x = c(4.5, 4.5),
        y = c(2.5, 4)
      ),
      aes(x = x, y = y),
      width = 0.2,
      rotate = 90,
      inherit.aes = FALSE,
      colour = "black",
      linewidth = 0.7
    ),
    geom_text(
      data = data.frame(
        effect_valence = factor("unpleasant", levels = ev_levels),
        x = 5.2,
        y = (2.5 + 4) / 2,
        label = "H4:P9"
      ),
      aes(x = x, y = y, label = label),
      fontface = "bold",
      inherit.aes = FALSE
    ),
    stat_brace(
      data = data.frame(
        effect_valence = factor("unpleasant", levels = ev_levels),
        x = c(0.7, 0.7),
        y = c(4, 5.5)
      ),
      aes(x = x, y = y),
      width = 0.2,
      rotate = 270,
      inherit.aes = FALSE,
      colour = "black",
      linewidth = 0.7
    ),
    geom_text(
      data = data.frame(
        effect_valence = factor("unpleasant", levels = ev_levels),
        x = 0.01,
        y = (4 + 5.5) / 2,
        label = "H4:P8"
      ),
      aes(x = x, y = y, label = label),
      fontface = "bold",
      inherit.aes = FALSE
    )
  )

(((hyp4_exp3_speaker + labs(title = "Collected (Exp 3)")) |
  (hyp4_exp3_pred_speaker_1 +
    labs(title = "Fictional (Exp 3 variant 1)") +
    fictional_transparency))) +
  plot_layout(guides = "collect", axis_titles = "collect_y") &
  theme(legend.position = "bottom")
```

#### Listener

`presc_normality ~ effect_valence`\
`stat_normality ~ effect_valence`

We expect:

  - **H4:P10**: Cause more likely to be prescriptively/statistically abnormal when outcome is unpleasant
  - **H4:P11**: Neutral outcomes do not help listener's inference of normality of C in either direction
  - **H4:P12**: Cause more likely to be prescriptively/statistically normal when outcome is pleasant

```{r hyp4-listener}
#| fig-height: 8
#| fig-cap: "Listener hears 'E because C' and infers whether C is prescriptively normal or abnormal. Data from Experiment 3 is collapsed over statistical normality of C, which was also manipulated in the experiment."

hyp4_plot_listener <- function(listener_trials, ylab) {
  plot <- listener_trials |>
    ggplot(aes(x = effect_valence, y = response, fill = effect_valence)) + # <- fill added
    stat_summary(fun = mean, geom = "col", width = 0.7) +
    stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
    scale_y_continuous(breaks = 1:7) +
    coord_cartesian(ylim = c(1, 7)) +
    scale_fill_manual(
      values = c(
        "pleasant" = CSP_colors[4],
        "neutral" = CSP_colors[1],
        "unpleasant" = CSP_colors[2]
      )
    ) +
    geom_hline(aes(yintercept = 4), linetype = 'dashed') +
    ylab(ylab) +
    xlab('Outcome valence') +
    theme_minimal()
  return(plot)
}
hyp4_plot_listener_pred <- function(listener_trials, ylab) {
  plot <- listener_trials |>
    ggplot(aes(x = effect_valence, y = response, fill = effect_valence)) + # <- fill added
    stat_summary(fun = mean, geom = "col", width = 0.7) +
    scale_y_continuous(breaks = 4) +
    coord_cartesian(ylim = c(1, 7)) +
    scale_x_discrete(
      expand = expansion(add = c(1, 1))
    ) +
    scale_fill_manual(
      values = c(
        "pleasant" = CSP_colors[4],
        "neutral" = CSP_colors[1],
        "unpleasant" = CSP_colors[2]
      )
    ) +
    geom_hline(aes(yintercept = 4), linetype = 'dashed') +
    ylab(ylab) +
    xlab('Outcome valence') +
    theme_minimal()
  return(plot)
}


preds <- list(geom_segment(
      data = data.frame(
        x = c(2.6, 0.6),
        xend = c(3.4, 1.4),
        y = c(5.5, 2.5),
        yend = c(5.5, 2.5)
      ),
      aes(x = x, xend = xend, y = y, yend = yend),
      linetype = "dashed",
      colour = "black",
      inherit.aes = FALSE
    ),
        stat_brace(
      data = data.frame(
        x = c(3.33, 3.33),
        y = c(4, 5.5)
      ),
      aes(x = x, y = y),
      width = 0.2,
      rotate = 90,
      inherit.aes = FALSE,
      colour = "black",
      linewidth = 0.7
    ),
    geom_text(
      data = data.frame(
        x = 3.73,
        y = (4 + 5.5) / 2,
        label = "H4:10"
      ),
      aes(x = x, y = y, label = label),
      fontface = "bold",
      inherit.aes = FALSE
    ),
        stat_brace(
      data = data.frame(
        x = c(0.66, 0.66),
        y = c(2.5, 4)
      ),
      aes(x = x, y = y),
      width = 0.2,
      rotate = 270,
      inherit.aes = FALSE,
      colour = "black",
      linewidth = 0.7
    ),
    geom_text(
      data = data.frame(
        x = 0.26,
        y = (2.5 + 4) / 2,
        label = "H4:12"
      ),
      aes(x = x, y = y, label = label),
      fontface = "bold",
      inherit.aes = FALSE
    ),
    geom_segment(
      data = data.frame(
        x = 2,
        xend = 2,
        y = 4,
        yend = 5
      ),
      aes(x = x, xend = xend, y = y, yend = yend),
      linewidth = 0.7,
      colour = "black",
      inherit.aes = FALSE
    ),
    geom_text(
      data = data.frame(
        x = 2,
        y = 5.2,
        label = "H4:P11"
      ),
      aes(x = x, y = y, label = label),
      fontface = "bold",
      inherit.aes = FALSE
    ))

hyp4_exp1_listener <- hyp4_plot_listener(
  exp1_listener_key_trials,
  ylab = "Inference that cause is prescriptively abnormal"
)
hyp4_exp1_pred_listener <- hyp4_plot_listener_pred(
  exp1_listener_params,
  ylab = "Inference that cause is prescriptively abnormal"
) + preds

hyp4_exp2_listener <- hyp4_plot_listener(
  exp2_listener_key_trials,
  ylab = "Inference that cause is statistically abnormal"
)
hyp4_exp2_pred_listener <- hyp4_plot_listener_pred(
  exp2_listener_params,
  ylab = "Inference that cause is statistically abnormal"
) + preds

((hyp4_exp1_listener +
    labs(title = "Collected (Exp 1)")) +
   (hyp4_exp1_pred_listener +
      labs(title = "Fictional (Exp 1)") +
      fictional_transparency) +
   (hyp4_exp2_listener +
      labs(title = "Collected (Exp 2)")) +
   (hyp4_exp2_pred_listener +
      labs(title = "Fictional (Exp 2)") +
      fictional_transparency)) +
  plot_layout(ncol = 2,guides = "collect",axes = "collect",axis_titles = "collect") &
  theme(legend.position = "bottom")
```


Making predictions for experiment 3 other than that neutral valence will not effect the inference is quite problematic. On the speaker part we are not making any predictions in SAPN and SNPA cases, and those are exactly those that the listener would be weighing against SNPN, and SAPA when making inferences.

We would have to commit to a stronger set of predictions such as that with pleasant outcome valence the positive effect due to SN and negative effect due to PA cancel out in such a way that the speaker still rates that higher than when we have double negative effect from both being abnormal. But anything close to that supported by the literature?

```{r hyp4-listener-exp3}
#| fig-cap: "Listener hears 'E because C' and infers whether C is prescriptively normal or abnormal. Data from Experiment 3 is collapsed over statistical normality of C, which was also manipulated in the experiment."

hyp4_exp3_plot_listener <- function(listener_trials, ylab) {
  plot <- listener_trials |>
    ggplot(aes(x = effect_valence, y = response, fill = effect_valence)) + # <- fill added
    stat_summary(fun = mean, geom = "col", width = 0.7) +
    stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
    scale_y_continuous(breaks = 1:7) +
    coord_cartesian(ylim = c(1, 7)) +
    scale_fill_manual(
      values = c(
        "pleasant" = CSP_colors[4],
        "neutral" = CSP_colors[1],
        "unpleasant" = CSP_colors[2]
      )
    ) +
    geom_hline(aes(yintercept = 4), linetype = 'dashed') +
    ylab(ylab) +
    xlab('Outcome valence') +
    theme_minimal() +
    facet_grid(. ~ stat_normality)
  return(plot)
}
hyp4_exp3_plot_listener_pred <- function(listener_trials, ylab) {
  plot <- listener_trials |>
    ggplot(aes(x = effect_valence, y = response, fill = effect_valence)) + # <- fill added
    stat_summary(fun = mean, geom = "col", width = 0.7) +
    scale_y_continuous(breaks = 4) +
    coord_cartesian(ylim = c(1, 7)) +
    scale_fill_manual(
      values = c(
        "pleasant" = CSP_colors[4],
        "neutral" = CSP_colors[1],
        "unpleasant" = CSP_colors[2]
      )
    ) +
    geom_hline(aes(yintercept = 4), linetype = 'dashed') +
    ylab(ylab) +
    xlab('Outcome valence') +
    theme_minimal() +
    facet_grid(. ~ stat_normality)
  return(plot)
}

hyp4_exp3_listener <- hyp4_exp3_plot_listener(
  exp3_listener_key_trials,
  ylab = "Inference that cause is prescriptively abnormal"
)
hyp4_exp3_pred_listener_1 <- hyp4_exp3_plot_listener_pred(
  exp3_listener_params_1,
  ylab = "Inference that cause is prescriptively abnormal"
)

hyp4_exp3_pred_listener_2 <- hyp4_exp3_plot_listener_pred(
  exp3_listener_params_2,
  ylab = "Inference that cause is prescriptively abnormal"
)

(((hyp4_exp3_listener + labs(title = "Collected (Exp 3)")) |
  (hyp4_exp3_pred_listener_1 +
    labs(title = "Fictional (Exp 3 variant 1)") +
    fictional_transparency)) |
  (hyp4_exp3_pred_listener_2 +
    labs(title = "Fictional (Exp 3 variant 2)") +
    fictional_transparency)) +
  plot_layout(guides = "collect", axis_titles = "collect_y") &
  theme(legend.position = "bottom")
```


### Hypothesis 5

#### Hyp1 w/ outcome valence

##### Speaker
`utterance_likelihood ~ presc_normality * mechanism * effect_valence`

```{r hyp1-speaker-valence}
#| fig-cap: "E: 'The machine made sound A.' C: 'A [COLOUR] marble was released.' Colour ([COLOUR] = red or blue) is counterbalanced with the norm manipulation: assignment of the normal and abnormal condition to each colour is randomised across participants."

# hyp1_speaker_valence <- hyp1_plot_speaker(
#   exp1_speaker_key_trials,
#   valence_facet = TRUE
# )
# hyp1_pred_speaker_valence <- hyp1_plot_speaker(
#   exp1_pred_speaker_trials,
#   valence_facet = TRUE
# )

# (hyp1_speaker_valence +
#   labs(title = "Collected") |
#   hyp1_pred_speaker_valence +
#     labs(title = "Fictional") +
#     fictional_transparency) +
#   plot_layout(guides = "collect") &
#   theme(legend.position = "bottom")
```

##### Listener
`presc_normality ~ mechanism * effect_valence`

```{r hyp1-listener-valence}
#| fig-cap: "Listener hears 'E because C' and infers whether C is prescriptively normal or abnormal."

# hyp1_listener_valence <- hyp1_plot_listener(
#   exp1_listener_key_trials,
#   valence_facet = TRUE
# )
# hyp1_pred_listener_valence <- hyp1_plot_listener(
#   exp1_pred_listener_trials,
#   valence_facet = TRUE
# )

# (hyp1_listener_valence +
#   labs(title = "Collected") |
#   hyp1_pred_listener_valence +
#     labs(title = "Fictional") +
#     fictional_transparency) +
#   plot_layout(guides = "collect") &
#   theme(legend.position = "bottom")
```

#### Hyp2 w/ outcome valence

##### Speaker

`utterance_likelihood ~ stat_normality * mechanism * effect_valence`
```{r hyp2-speaker-valence}
#| fig-cap: "E: 'The machine made sound A.' C: 'A [COLOUR] marble was released.' Colour ([COLOUR] = red or blue) is counterbalanced with the norm manipulation: assignment of the normal and abnormal condition to each colour is randomised across participants."

# hyp2_speaker_valence <- hyp2_plot_speaker(
#   exp2_speaker_key_trials,
#   valence_facet = TRUE
# )
# hyp2_pred_speaker_valence <- hyp2_plot_speaker(
#   exp2_pred_speaker_trials,
#   valence_facet = TRUE
# )

# (hyp2_speaker_valence +
#   labs(title = "Collected") |
#   hyp2_pred_speaker_valence +
#     labs(title = "Fictional") +
#     fictional_transparency) +
#   plot_layout(guides = "collect") &
#   theme(legend.position = "bottom")
```

##### Listener

`stat_normality ~ mechanism * effect_valence`

```{r hyp2-listener-valence}
#| fig-cap: "Listener hears 'E because C' and infers whether C is statistically normal or abnormal."

# hyp2_listener_valence <- hyp2_plot_listener(
#   exp2_listener_key_trials,
#   valence_facet = TRUE
# )
# hyp2_pred_listener_valence <- hyp2_plot_listener(
#   exp2_pred_listener_trials,
#   valence_facet = TRUE
# )

# (hyp2_listener_valence +
#   labs(title = "Collected") |
#   hyp2_pred_listener_valence +
#     labs(title = "Fictional") +
#     fictional_transparency) +
#   plot_layout(guides = "collect") &
#   theme(legend.position = "bottom")
```

#### Hyp3 w/ outcome valence

##### Speaker

`utterance_likelihood ~ stat_normality * presc_normality * mechanism * effect_valence`

```{r hyp3-speaker-valence}
#| fig-cap: "SA - Statistically abnormal, SN - Statistically normal, PA - Prescriptively abnormal, PN - Prescriptively normal. E: 'The machine made sound A.' C: 'A [COLOUR] marble was released.' Colour ([COLOUR] = red or blue) is counterbalanced with the norm manipulation: assignment of the normal and abnormal condition to each colour is randomised across participants.  C is subject to both statistical and prescriptive norms."

# hyp3_speaker_valence <- hyp3_plot_speaker(
#   exp3_speaker_key_trials,
#   valence_facet = TRUE
# )
# hyp3_pred_speaker_valence <- hyp3_plot_speaker(
#   exp3_pred_speaker_trials,
#   valence_facet = TRUE
# )

# (hyp3_speaker_valence +
#   labs(title = "Collected") |
#   hyp3_pred_speaker_valence +
#     labs(title = "Fictional") +
#     fictional_transparency) +
#   plot_layout(guides = "collect") &
#   theme(legend.position = "bottom")
```

##### Listener

`presc_normality ~ stat_normality * mechanism * effect_valence`

```{r hyp3-listener-valence}
#| fig-cap: "With the knowledge of statistical norm held by the speaker, the listener hears 'E because C' and infers whether C is prescriptively normal or abnormal."

# hyp3_listener_valence <- hyp3_plot_listener(
#   exp3_listener_key_trials,
#   valence_facet = TRUE
# )
# hyp3_pred_listener_valence <- hyp3_plot_listener(
#   exp3_pred_listener_trials,
#   valence_facet = TRUE
# )

# (hyp3_listener_valence +
#   labs(title = "Collected") |
#   hyp3_pred_listener_valence +
#     labs(title = "Fictional") +
#     fictional_transparency) +
#   plot_layout(guides = "collect") &
#   theme(legend.position = "bottom")
```


## Statistical Analysis
